
# Aim
```{r}
# ==================================================================
# Summary: PCA-Based Analysis of Antibiotic-Isolate Relationships
# ==================================================================
# Aim:
# This script evaluates relationships in PCA space, focusing on:
# 1. Rows: Isolates vs. Columns: Drugs
# 
# Methodology:
# - Uses imputation (missMDA) for handling missing values.
# - Generates a correlation matrix without imputation.
# - Performs PCA on antibiotic conditions and isolates.
# - Visualizes PCA distributions using scatter plots.
# - Computes and analyzes a correlation matrix for drugs.
# - Examines PCA clustering based on antibiotic mechanism of action.
# - Merges PCA results with species and clinical metadata.
# - Outputs various visualizations in PDF format.

# Key Outputs:
# - Waterfall plot showing missing data distribution.
# - PCA plots for conditions (drugs) and isolates.
# - Correlation matrix PCA for drugs and isolates.
# - PCA clustering based on antibiotic mechanisms.
# - Integration of clinical metadata for further insights.

# Next Steps:
# - Optimize missing data handling strategies.
# - Explore additional PCA components.
# - Validate clustering results with external metadata.

```



#1. Defining variables
```{r setup, include=FALSE}

genDir <- getwd() 


#Pop data variables
data.dir <- c("ASCT_Experimental_Results/ASCT_2_curated_PCA")
res.dir <- c("ASCT_Experimental_Results/ASCT_4_Figures")

exp.res.dir <- c(paste(genDir,
                       "/",
                       "ASCT_Experimental_Results/ASCT_4_Figures",sep=""))
wdDir <- genDir

res.dir <- paste(genDir,"/",res.dir ,sep="")
data.dir <- paste(genDir,"/",data.dir,sep="")
setwd(wdDir)

# list the experiment directories to pull the tracking data
# Get today's date
today <- Sys.Date()

# Format the date as YYYYMMDD
formatted_date <- format(today, "%Y%m%d")


# EDIT the time scale axis that should be used 
plot.xaxis.time.scale <- c(0,12,24,36,48,60,72)

```

#2. Loading packages
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels) 
library(MESS)
library(gghighlight)
library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)
library(stringr)


# Dealing with missing values
#install.packages("missMDA")
library(missMDA)
# Link to website on how to use miss MDA http://factominer.free.fr/missMDA/PCA.html
library(ggcorrplot)

library(data.table)
library(FactoMineR)  # Link to website on how to use miss MDA http://factominer.free.fr/missMDA/PCA.html



```

#3. Load all PCA exl data
```{r}

#Creacting vector with the list of file names
PCA.list <- list.files(path = data.dir ,
                            pattern = "_GTManual.HR.R.growth_1_2_Killing_Features_PCAexl_MD.0sd_PCAstr.allLCF_",
                            full.names = FALSE)

#setting path to where all the csv files due to be processed are
#setwd(i)

path.to.data <- ("/Users/Alex/Documents/PhD/PhD_project/PhD_project-Tolerance/R-ANALYSIS/Ranalysis_perwell/Ranalysis_perWell_TLKK/ASCT_Analysis_AJ_orginal/ASCT_EXPERIMENTS_v2-critical/ASCT.Ranalysis_KF_Variability_PCA_Statistics/ASCT_Experimental_Results/ASCT_2_curated_PCA/")

#i <- PCA.list[1]

KF.df <- data.frame()
for ( i in PCA.list) {
  
  
  kf.sub <- read.csv(paste(path.to.data,
                           i,
                           sep=""))
  
  kf.sub <- kf.sub %>%
      select(Isolate,
             contains("Trkv2_Ila2BaSic_AUCrt_0.72h_"))

  
  kf.sub <- melt(  kf.sub , variable.name = "Feature",
                   value.name = "value")
    
  KF.df <- rbind(KF.df,
                 kf.sub)
    
}

rm(kf.sub)

```

##3.1 data wrangling 
```{r}

KF.df<- separate(KF.df, col = "Feature", 
                  into =c("Abx.con",
                          "Tracking",
                          "Ilastik",
                          "AUCrt",
                          "AUCrtrange",
                          "ExpID"),
                          
                          sep="_")
 

KF.df<- KF.df %>%
  mutate(Killing.Definiton = paste(Tracking,
                                   Ilastik,
                                   sep="_"),
         Killing.Feature = paste(AUCrt,
                                 AUCrtrange,
                                 sep="_") )%>%
  select(ExpID,
         Isolate,
         Abx.con,
        
         Killing.Definiton,
         Killing.Feature,
         value)



```

## 3.2 Waterfall plot of the amount of NAs
```{r}

KF.df.NAs <- KF.df %>%
    filter(Abx.con != "BDQ.20x")%>%
  ungroup()%>%
  group_by(Isolate)%>%
    mutate(value_NAs = sum(is.na(value)))%>%
  ungroup()%>%
  select(Isolate,
         value_NAs)%>%
  distinct()%>%
  group_by(value_NAs)%>%
  mutate(Number.Isolate = 1)%>%
  mutate(Number.Isolate = sum (Number.Isolate))%>%
  ungroup()%>%
  mutate(Percentage.Missing = (Number.Isolate / 416)*100)



plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_MissingData_",formatted_date,".pdf", sep = "")

pdf(plot.name)
 KF.df.NAs %>%
  select(value_NAs,
         Number.Isolate,
         Percentage.Missing) %>%
  distinct() %>%
  ggplot(aes(y = Number.Isolate,
             x = value_NAs,
             label = paste0(round(Percentage.Missing,3) , "%"))) +
     scale_x_continuous(limits = c(-1, 20), breaks = seq(0, 20, by = 1)) +

  geom_bar(stat = "identity") +
   theme_prism()+
  labs(x = "Number of NAs",
       y = "Number of Isolates",
       title = "Barplot of missing values",
       caption = "Percentage of Missing Data") +
    geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 dev.off()

 
 
 Isolates.present.in.Alldrugs <- KF.df.NAs %>%
   filter(value_NAs == 0 )
 
 
  Isolates.present.in.Alldrugs <- unique( Isolates.present.in.Alldrugs$Isolate)  
```

 
#4. PCA of only isolates present in all abx 
```{r}

KF.df.100.present <- KF.df %>%
    filter(Abx.con != "BDQ.20x")%>%
  filter(Isolate %in%  Isolates.present.in.Alldrugs)%>%
          select(
                 Abx.con,
                 Isolate,
                 value)%>%
          spread(Isolate,
                 value)


Abx.list <- KF.df.100.present$Abx.con

KF.df.100.present <- KF.df.100.present %>%
  select(-Abx.con)


# Perform PCA
pca <- prcomp(KF.df.100.present, scale = TRUE)

# Extract PCA scores
scores <- as.data.frame(pca$x[, 1:2])


# Calculate the proportion of variance for PC1 and PC2
variance_explained <- pca$sdev^2 / sum(pca$sdev^2)
variance_pc1 <- variance_explained[1]*100
variance_pc2 <- variance_explained[2]*100


scores$Abx.con <- Abx.list
scores$var.pc1 <- variance_pc1
scores$var.pc2 <- variance_pc2

PCA.row.Abx_col.Iso.CONDpca.100present <- scores

library(stringr)
PCA.row.Abx_col.Iso.CONDpca.100present <-PCA.row.Abx_col.Iso.CONDpca.100present %>%
  mutate(Abx = str_extract(Abx.con, "^[^.]+"))%>%
  mutate(Abx = if_else(Abx == "IPMb", "IPM",
                       if_else(Abx == "IPMc", "IPM",
                               if_else(Abx == "MXFb", "MXF", Abx))))%>%
mutate(Concentration = str_extract(Abx.con, "(?<=\\.).*"))



plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_drugs.V.Iso-CONDITIONpca.Completly.present_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.row.Abx_col.Iso.CONDpca.100present %>%
  ggplot(aes(x = PC1,
             y = PC2,
             colour = Abx,
             label = Abx.con)) +
  
  geom_point(size = 1,
             stroke = 0) +
  geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
     theme(aspect.ratio = 1)+
   labs(x = paste("PC1 (", round(unique(PCA.row.Abx_col.Iso.CONDpca.100present$var.pc1),3), "%)" ,sep=""),
       y = paste("PC2 (", round(unique(PCA.row.Abx_col.Iso.CONDpca.100present$var.pc2),3), "%)",sep=""),
       title = "PCA conditions",
       caption = paste("All iso present across all drugs (n", length(Isolates.present.in.Alldrugs), ")")) +

  theme_prism()+
   theme(legend.position = "none")
dev.off()


```


#5. Imputation (missMDA)
## 5.1 Handeling Nas in data
### 5.1.1  Imputation and PCA with missing values
```{r}

Isolates.with.max.3missing.values <- KF.df.NAs %>%
  filter(value_NAs <= 3)%>%
  select(Isolate)%>%
  distinct()

Isolates.with.max.3missing.values <- Isolates.with.max.3missing.values$Isolate



KF.df.na <- KF.df %>%
  filter(Isolate %in% Isolates.with.max.3missing.values )%>%
          select(
                 Abx.con,
                 Isolate,
                 value)%>%
          spread(Isolate,
                 value)


 # Link to website on how to use miss MDA http://factominer.free.fr/missMDA/PCA.html
KF.df.na.main <- KF.df.na %>%
  filter(Abx.con != "BDQ.20x")%>%
  select(-Abx.con)

Abx.list <- KF.df.na$Abx.con
Abx.list <- Abx.list[Abx.list != "BDQ.20x"]
#---

nb <- estim_ncpPCA(KF.df.na.main, scale =TRUE)
nb <-nb[["ncp"]]


comp <- imputePCA(KF.df.na.main, ncp = nb, scale = TRUE)

mi <- MIPCA(KF.df.na.main, scale = TRUE , ncp = nb)
KF.df.na.Imputed.Conditions <- data.frame(comp$completeObs)

# Perform PCA
pca <- prcomp(KF.df.na.Imputed.Conditions, scale = TRUE)

# Extract PCA scores
scores <- as.data.frame(pca$x[, 1:2])


# Calculate the proportion of variance for PC1 and PC2
variance_explained <- pca$sdev^2 / sum(pca$sdev^2)
variance_pc1 <- variance_explained[1]*100
variance_pc2 <- variance_explained[2]*100


scores$Abx.con <- Abx.list
scores$var.pc1 <- variance_pc1
scores$var.pc2 <- variance_pc2

PCA.row.Abx_col.Iso.CONDpca <- scores

library(stringr)
PCA.row.Abx_col.Iso.CONDpca <-PCA.row.Abx_col.Iso.CONDpca%>%
  mutate(Abx = str_extract(Abx.con, "^[^.]+"))%>%
  mutate(Abx = if_else(Abx == "IPMb", "IPM",
                       if_else(Abx == "IPMc", "IPM",
                               if_else(Abx == "MXFb", "MXF", Abx))))%>%
mutate(Concentration = str_extract(Abx.con, "(?<=\\.).*"))



plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_drugs.V.Iso-CONDITIONpca.3missing_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.row.Abx_col.Iso.CONDpca %>%
  ggplot(aes(x = PC1,
             y = PC2,
             colour = Abx,
             label = Abx.con)) +
  geom_point() +
  geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
     theme(aspect.ratio = 1)+

  theme_prism()+
   labs(x = paste("PC1 (", round(unique(PCA.row.Abx_col.Iso.CONDpca $var.pc1),3), "%)" ,sep=""),
       y = paste("PC2 (", round(unique(PCA.row.Abx_col.Iso.CONDpca $var.pc2),3), "%)",sep=""),
       title = "PCA conditions using imputation",
       caption = paste("Isolates with max 3 missing values across all drugs (n", length(Isolates.with.max.3missing.values), ")")) +
   theme(legend.position = "none")
dev.off()


#Housekeeping
rm(mi,
   comp,
   pca,
   scores)
```


###5.1.2 PCA Iso.Rows Drugs Cols PCAiso
```{r}
# Link to website on how to use miss MDA http://factominer.free.fr/missMDA/PCA.html
KF.df.na.main.Iso <- KF.df.na %>%
  filter(Abx.con != "BDQ.20x")%>%
  select(-Abx.con)

Abx.list <- KF.df.na$Abx.con
Abx.list <- Abx.list[Abx.list != "BDQ.20x"]


KF.df.na.main.Iso <- data.frame(t(KF.df.na.main.Iso))


# Rename variables
names(KF.df.na.main.Iso) <- Abx.list

nb <- estim_ncpPCA(KF.df.na.main.Iso, scale =TRUE)
nb <-nb[["ncp"]]


comp <- imputePCA(KF.df.na.main.Iso, ncp = nb, scale = TRUE)

KF.df.na.Imputed.Conditions <- data.frame(comp$completeObs)

# Perform PCA
pca <- prcomp(KF.df.na.Imputed.Conditions, scale = TRUE)

# Extract PCA scores
scores <- as.data.frame(pca$x[, 1:2])


# Calculate the proportion of variance for PC1 and PC2
variance_explained <- pca$sdev^2 / sum(pca$sdev^2)
variance_pc1 <- variance_explained[1]*100
variance_pc2 <- variance_explained[2]*100



scores$Isolate <- rownames(scores)

rownames(scores) <- NULL


scores$var.pc1 <- variance_pc1
scores$var.pc2 <- variance_pc2

PCA.row.Iso_col.Abx.ISOpca <- scores


plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_Iso.V.drug_ISOLATEpca_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.row.Iso_col.Abx.ISOpca %>%
  ggplot(aes(x = PC1,
             y = PC2)) +
  geom_point(alpha = 0.25,
             stroke = 0) +
     theme(aspect.ratio = 1)+

  theme_prism()+
   theme(legend.position = "none")
dev.off()

```



#6. Species Infromation
```{r}

Species.Info <- read.csv("/Users/Alex/Documents/PhD/PhD_project/PhD_project-Tolerance/R-ANALYSIS/Ranalysis_perwell/Ranalysis_perWell_TLKK/ASCT_Analysis_AJ_orginal/ASCT_EXPERIMENTS_v2-critical/ASCT.Ranalysis_Exp_Info/ASCT_Label_directory/ClinicalIsolates_LookUpMasterList_BWupdated.csv")

Species.Info <- Species.Info%>%
   mutate( Isolate = paste("Iso.",Sample_ID_Full,
                         sep=""))%>%
  mutate(Isolate = sub(" ","",Isolate))%>%
  select(Isolate,
         Subspecies)%>%
  mutate(Isolate = if_else(Isolate == "Iso.ATCC","Iso.ATc.19979", Isolate ))

```

#7. Clinical Metadata 
```{r}


MD.df <- read.csv("/Users/Alex/Documents/PhD/PhD_project/PhD_project-Tolerance/R-ANALYSIS/Ranalysis_perwell/Ranalysis_perWell_TLKK/ASCT_Analysis_AJ_orginal/ASCT_EXPERIMENTS_v2-critical/ASCT.Ranalysis_Exp_Info/ASCT_Clinical_Metadata/ASCT_3_Clinical_Metadata_forAlex.csv")



MD.df <- MD.df %>%
    mutate(ClearedVSpersistant_ATS = as.numeric(ClearedVSpersistant_ATS))%>%
   mutate(ClearedVSpersistant_ATS = if_else(ClearedVSpersistant_ATS == 2, "Persistant.Inf",
                                     if_else(ClearedVSpersistant_ATS == 1, "Cleared.Inf" ,NA)))%>%
    mutate(FEV1_clearPers = ifelse(FEV1_clearPers == "ND" | FEV1_clearPers == "", NA, as.numeric(FEV1_clearPers)))%>%

  select(Isolate, 
         ClearedVSpersistant_ATS,
          FEV1_clearPers)%>%
  mutate(Isolate = paste("Iso.", Isolate,sep=""))%>%
    mutate(Isolate = sub(" ","",Isolate))%>%

    mutate(Isolate = if_else(Isolate == "Iso.ATCC","Iso.ATc.19979", Isolate ))


```

## 7.1 Merging data
```{r}

PCA.row.Iso_col.Abx.ISOpca <- PCA.row.Iso_col.Abx.ISOpca %>%
  left_join(MD.df, by = "Isolate")

PCA.row.Iso_col.Abx.ISOpca <- PCA.row.Iso_col.Abx.ISOpca %>%
  left_join(Species.Info , by = "Isolate")

```


```{r}
plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_Iso.V.drug_ISOLATEpca-LabSpecies_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.row.Iso_col.Abx.ISOpca %>%
  filter(Subspecies != "")%>%
  ggplot(aes(x = PC1,
             y = PC2, 
             colour = Subspecies)) +
  geom_point(alpha = 0.25,
             stroke = 0) +
     theme(aspect.ratio = 1)+

  theme_prism()
dev.off()
```


```{r}
plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_Iso.V.drug_ISOLATEpca-LabOutcome_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.row.Iso_col.Abx.ISOpca %>%
filter(!is.na(ClearedVSpersistant_ATS))%>%
  ggplot(aes(x = PC1,
             y = PC2, 
             colour = ClearedVSpersistant_ATS)) +
  geom_point(alpha = 0.25,
             stroke = 0) +
     theme(aspect.ratio = 1)+

  theme_prism()
dev.off()
```

#Houskeeping
```{r}
rm(comp,
   pca,
   scores,
   PCA.row.Abx_col.Iso.CONDpca,
   PCA.row.Abx_col.Iso.CONDpca.100present,
   PCA.row.Iso_col.Abx.ISOpca)
```

#8. Correlation matrix based PCA
```{r}
# Applying correlation function
Corr.matrix <- cor(KF.df.na.main.Iso,
               use = "pairwise.complete.obs",
               method ="pearson") # Default is pearsons correlation
```

##8.1 Visualizing correlation matrix
```{r}
# Visualizing correlation matrix
plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_KF_PairedCorrMatrix_Drugs_",formatted_date,".pdf", sep = "")

pdf(plot.name)
ggcorrplot(Corr.matrix,
           hc.order = TRUE, #logical value. If TRUE, correlation matrix will be hc.ordered using hclust function.
           lab = TRUE,
            lab_size = 0.8,    # Adjust the size of correlation coefficient labels
  tl.cex = 4 ,# Adjust the size of variable names
  title =  "Pairwise correlation matrix across all drugs",
  legend.title = "Peasons corr.coeff"
  )    
dev.off()
```



 Remarks
 - Clofazamins poorly correlates across the two CLO antibiotic concentrations.
 - AZM, AMK, LZD ,TGC and MIN have a relatively strong correlation coefficient between each other. However, a poor correlation with IPM , FOX and CLO. A moderate/low coefficient is observed considering MXF


##8.2 Applying PCA analysis on correlation matrix
```{r}

# Perform PCA
pca <- prcomp(Corr.matrix, scale = TRUE)

# Extract PCA scores
scores <- as.data.frame(pca$x[, 1:2])


# Calculate the proportion of variance for PC1 and PC2
variance_explained <- pca$sdev^2 / sum(pca$sdev^2)
variance_pc1 <- variance_explained[1]*100
variance_pc2 <- variance_explained[2]*100


scores$Abx.con <- Abx.list
scores$var.pc1 <- variance_pc1
scores$var.pc2 <- variance_pc2

PCA.corr.Matrix <- scores

library(stringr)
PCA.corr.Matrix  <-PCA.corr.Matrix %>%
  mutate(Abx = str_extract(Abx.con, "^[^.]+"))%>%
  mutate(Abx = if_else(Abx == "IPMb", "IPM",
                       if_else(Abx == "IPMc", "IPM",
                               if_else(Abx == "MXFb", "MXF", Abx))))%>%
mutate(Concentration = str_extract(Abx.con, "(?<=\\.).*"))




plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_CorrMatrix_ConditionPCA_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.corr.Matrix %>%

  ggplot(aes(x = PC1,
             y = PC2,
             colour = Abx,
             label = Abx.con)) +
  
  geom_point(size = 1,
             stroke = 0) +
  geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
     theme(aspect.ratio = 1)+
   labs(x = paste("PC1 (", round(unique(PCA.corr.Matrix$var.pc1),3), "%)" ,sep=""),
       y = paste("PC2 (", round(unique(PCA.corr.Matrix $var.pc2),3), "%)",sep=""),
       title = "PCA of conditions using correlation matrix",
       subtitle =  "Each colour represents an antibiotic",
       colour = "Antibiotic") +
    theme_prism()+
   theme(legend.position = "none")+

  theme(plot.caption = element_text(size = 3, margin = margin(t = 10, r = 10, b = 10, l = 10)))

dev.off()



```



### Adding infomation on mechnaism of action 
```{r}

plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_CorrMatrix_ConditionPCA-mechanism_",formatted_date,".pdf", sep = "")

pdf(plot.name)
PCA.corr.Matrix %>%
  mutate(Mechanism.of.action.target = if_else(Abx == "IPM" | Abx == "FOX", "Cell wall",
                                              if_else(Abx == "MIN" | Abx == "AZM" | Abx == "AMK" | Abx == "TGC" | Abx == "LZD" , "RNA protein synthesis",
                                                      if_else(Abx == "MXF", "DNA replication",
                                                              if_else(Abx == "CLO", "Unknown" , "Unknown")))))%>%
  ggplot(aes(x = PC1,
             y = PC2,
             colour = Mechanism.of.action.target,
             label = Abx.con)) +
  
  geom_point(size = 1,
             stroke = 0) +
  geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
     theme(aspect.ratio = 1)+
   labs(x = paste("PC1 (", round(unique(PCA.corr.Matrix$var.pc1),3), "%)" ,sep=""),
       y = paste("PC2 (", round(unique(PCA.corr.Matrix $var.pc2),3), "%)",sep=""),
       title = "PCA of conditions using correlation matrix",
       subtitle =  "Each colour represents a mechanism of action (MoA)",
       caption =  "The mechnism(s) of action of clofazamine remains unclear. Some suggest it binds to bacterial DNA inhibiting replication while others belive its antimicrobial acrivity appears to be membrane directed.",
       colour = "MoA") +
  

    theme_prism()+
   theme(legend.position = "bottom")+

  theme(plot.caption = element_text(size = 3, margin = margin(t = 10, r = 10, b = 10, l = 10)))

dev.off()


#Housekeeping
rm(ggp1,
   kmeans_clust,
   pca,
   pca_scores,
   res.pca)
```


# 9. Correlation matrix PCA 
```{r}
library(data.table)
library(FactoMineR)


# Make Transpose this dataframe 
Transposed.rowAbx.colIso <- transpose(KF.df.na.main.Iso)


# get row and colnames in order
colnames(Transposed.rowAbx.colIso) <- rownames(KF.df.na.main.Iso)
rownames(Transposed.rowAbx.colIso) <- colnames(KF.df.na.main.Iso)


# Applying correlation function
Corr.matrix.colIso <- cor(Transposed.rowAbx.colIso,
               use = "pairwise.complete.obs",
               method ="pearson") # Default is pearsons correlation


# Perform PCA
pca.ISO <- prcomp(Corr.matrix.colIso , scale = TRUE)

# Extract PCA scores
scores <- as.data.frame(pca.ISO$x[,1:2])


# Calculate the proportion of variance for PC1 and PC2
variance_explained <- pca.ISO$sdev^2 / sum(pca.ISO$sdev^2)

variance_pc1 <- variance_explained[1]*100
variance_pc2 <- variance_explained[2]*100


# PCA of isolate vs drugs ; 
scores$Isolate <- names(Transposed.rowAbx.colIso)
scores$var.pc1 <- variance_pc1
scores$var.pc2 <- variance_pc2

pca.ISO.corr.Matrix <- scores




plot.name <- paste(exp.res.dir,"/PCA-analysis_Drug.V.Iso/","ASCT_PCA_CorrMatrix_IsoPCA_",formatted_date,".pdf", sep = "")

pdf(plot.name)
pca.ISO.corr.Matrix%>%

  ggplot(aes(x = PC1,
             y = PC2,
             label = Isolate)) +
  
  geom_point(size = 1,
             stroke = 0,
             alpha = 0.20) +
  geom_text(size = 1, color = "black", vjust = -0.5) +  # Adjust size and vjust
     theme(aspect.ratio = 1)+
   labs(x = paste("PC1 (", round(unique(pca.ISO.corr.Matrix$var.pc1),3), "%)" ,sep=""),
       y = paste("PC2 (", round(unique(pca.ISO.corr.Matrix$var.pc2),3), "%)",sep=""),
       title = "PCA of Iso using correlation matrix") +
  

    theme_prism()+
   theme(legend.position = "none")+

  theme(plot.caption = element_text(size = 3, margin = margin(t = 10, r = 10, b = 10, l = 10)))

dev.off()
```

