---
title: "ASCT_Val3.2_POC"
output: html_document
date: "2024-08-02"
---
# ================================================================
# Aim
# ================================================================
# Quantify how well ilastik pixel classification matches the
# curated “ground truth” segmentation using the Jaccard index (IoU).

# Functionality:
# - Loads IoU results per field, per frame and per ROI from multiple
#   evaluation directories.
# - Cleans/standardizes experiment IDs and timesteps.
# - Summarizes IoU distributions across time (0, 24, 48, 72 h) and
# - Generates publication-style boxplots/violin plots of IoU values.
# - Computes N of ROIs + mean/median IoU per timepoint and exports a
#   formatted text report for the supplement.


# 1. Define variables
```{r}


info.wdDir <- getwd()
info.resDir <- paste(info.wdDir,
                     "/Results",
                     sep ="")

#---- Path to IoU per Field per SC VS and OFFC class ----
  ## Go back one level from the current working directory
  setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("Segmentation_Evaluation_PerField")
  setwd("IoU_Results_SC.VS.OFFC_Jaccard.Index")

  ## Get the current working directory
  info.IoUDir.PerField.SCVSOFFC <- getwd()
  
  setwd(info.IoUDir.PerField.SCVSOFFC )
  
  

#---- Path to IoU per Field all segments class ----
  
  setwd(info.wdDir)
  
  ## Go back one level from the current working directory
  setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("Segmentation_Evaluation_PerField")
  setwd("PC_Jaccard.Index")

  ## Get the current working directory
  info.IoUDir.PerField.allSeg <- getwd()
  
  setwd(info.IoUDir.PerField.allSeg)
  
  
  
  
#---- Path to IoU per Field per class per ROI ----
  
  setwd(info.wdDir)
  
  ## Go back one level from the current working directory
  setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("Segmentation_Evaluation_PerField_perFrame_perROI")
 # setwd("IoU_Results/Results_TO_be_USED")
  setwd("IoU_Results")

  ## Get the current working directory
  info.IoUDir.PerField.perROI <- getwd()
  
  setwd(  info.IoUDir.PerField.perROI)
  
  

```

# 2. load libraries
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)

library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)
library(stringr)

library(ggExtra)
library(grid)  # Load the grid package allows you to add text to pages in ggplot

# For classification assement
library(caret)
```

# 2. Loading data
## 2.1 Loading PC evalauation per field per frame all segments
```{r}
IoU.perField.allSeg.df <- data.frame()

  setwd(info.IoUDir.PerField.allSeg)
  # List all files in the current directory
    files <- list.files(info.IoUDir.PerField.allSeg)
    
  # Loop through each of the CSV files and read them
  for (csv_file in files) {
    
    # Read the CSV file
    IoU.perField.allSeg.df.sub <- read.csv(csv_file)
    IoU.perField.allSeg.df.sub <- IoU.perField.allSeg.df.sub %>%
       mutate(timestep = X)%>%
       mutate(ExpID = gsub("_perField_allSegements_JaccardIndex.csv", "",csv_file))%>%
       select(ExpID,
              timestep,
              Jaccard_Index)
    
  # Combine the data from the CSV file with the main data frame
  IoU.perField.allSeg.df <- rbind(IoU.perField.allSeg.df, IoU.perField.allSeg.df.sub)
  
  rm(IoU.perField.allSeg.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       csv_files)

```

## 2.2 Loading SC VS OFFC
```{r}
IoU.perField.SC.VS.OFFC.df <- data.frame()

  setwd(info.IoUDir.PerField.SCVSOFFC)
  # List all files in the current directory
    files <- list.files(info.IoUDir.PerField.SCVSOFFC)
    
    
  # Loop through each of the CSV files and read them
  for (csv_file in files) {
    
      setwd(info.IoUDir.PerField.SCVSOFFC)
    
    # Read the CSV file
    IoU.perField.SC.VS.OFFC.df.sub <- read.csv(csv_file)
    
    
    IoU.perField.SC.VS.OFFC.df.sub <- IoU.perField.SC.VS.OFFC.df.sub %>%
       mutate(timestep = X)%>%
       mutate(ExpID = gsub("_BFgt_one_hot_MERGED.tif_perField_allSegements_JaccardIndex.csv", "",csv_file))%>%
             mutate(ExpID = gsub("MOC-", "",ExpID))%>%

       select(ExpID,
              timestep,
              Jaccard_Index)
    
  # Combine the data from the CSV file with the main data frame
  IoU.perField.SC.VS.OFFC.df <- rbind(IoU.perField.SC.VS.OFFC.df,
                                      IoU.perField.SC.VS.OFFC.df.sub)
  
  rm(IoU.perField.SC.VS.OFFC.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       csv_files)

```



## 2.2 Loading ROIs IoUs
```{r}
IoU.perField.perROI.df <- data.frame()

  setwd(info.IoUDir.PerField.perROI)
  # List all files in the current directory
    files <- list.files(info.IoUDir.PerField.perROI)
    
           files <- files[grep("_JaccardIndex.csv$", files)]

  # Loop through each of the CSV files and read them
  for (csv_file in files) {
    
      setwd(info.IoUDir.PerField.perROI)
    
    # Read the CSV file
    IoU.perField.perROI.df.sub <- read.csv(csv_file)
    
    
    IoU.perField.perROI.df.sub <- IoU.perField.perROI.df.sub %>%
      filter(Area == 0)%>%
      select(Jaccard_Index)%>%
      mutate(ROI = 1)%>%
      mutate(ROI = cumsum(ROI))%>%
      select(ROI,
             Jaccard_Index)%>%
       mutate(ExpID = gsub("MOC-0_24_48_72h_", "",csv_file),
              ExpID = gsub("_BF_one_hot_MERGED__", "",ExpID),
              ExpID = gsub("_BF_one_hot_MERGED_", "",ExpID),
              
              ExpID = gsub("_JaccardIndex.csv", "",ExpID))%>%
  mutate(timestep = str_extract(ExpID, "(?<=frame_)\\d+"),
                  ExpID= str_extract(ExpID, ".*(?=frame)")) %>% # Keep everything before "frame"

       select(ExpID,
              timestep,
              ROI,
              Jaccard_Index)
    
  # Combine the data from the CSV file with the main data frame
  IoU.perField.perROI.df <- rbind(IoU.perField.perROI.df,
                                      IoU.perField.perROI.df.sub)
  
  rm(IoU.perField.perROI.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       files)

```

# 3. Plot
## 3.1 All segments per field per frame
```{r}
# Create an integrated plot with both boxplot and density plot for Jaccard_Index
IoU.perField.allSeg.df.plot <- IoU.perField.allSeg.df%>%
  ggplot(aes(x = Jaccard_Index)) +
  geom_boxplot(aes(y = 18), fill = "black", alpha = 0.5, outlier.shape = NA) + # Boxplot without outliers
  geom_jitter(aes(y = 18), width = 0.1, color = "black", alpha = 0.2,shape = 20 , size = 1) + # Jittered points inside the boxplot
  geom_density(aes(y = ..density..), fill = "black", alpha = 0.5) + # Density plot
  theme_prism(base_line_size = 8/14) +
  scale_x_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, by = 0.1)) + # Set x-axis from 0 to 1 with 0.1 intervals
  theme(   aspect.ratio = 1)+
  labs(title = "Jaccard Index per Field per Frame (all segments)",
       x = "IoU",
       y = "Frequency")

# Save the plot as a PDF
ggsave(paste(info.resDir ,"/Jaccard_Index_perField_allSeg_Plot.pdf",sep=""), plot = IoU.perField.allSeg.df.plot  , width = 8, height = 6, device = "pdf")

```

## 3.2 SC VS OFFC segments per field per frame
```{r}
# Create an integrated plot with both boxplot and density plot for Jaccard_Index
IoU.perField.SC.VS.OFFC.df.plot <- IoU.perField.SC.VS.OFFC.df%>%
  ggplot(aes(x = Jaccard_Index)) +
  geom_boxplot(aes(y = 18), fill = "black", alpha = 0.5, outlier.shape = NA) + # Boxplot without outliers
  geom_jitter(aes(y = 18), width = 0.1, color = "black", alpha = 0.2,shape = 20 , size = 1) + # Jittered points inside the boxplot
  geom_density(aes(y = ..density..), fill = "black", alpha = 0.5) + # Density plot
  theme_prism(base_line_size = 8/14) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) + # Set x-axis from 0 to 1 with 0.1 intervals
  labs(title = "Jaccard Index per Field per Frame (SC VS OFFC segments)",
       x = "IoU",
       y = "Frequency")
# Save the plot as a PDF
ggsave(paste(info.resDir ,"/Jaccard_Index_perField_sc.vs.offc_Plot.pdf",sep=""), plot = IoU.perField.SC.VS.OFFC.df.plot   , width = 8, height = 6, device = "pdf")

```


## 3.2 ROI per Frame per Field

```{r}
# Create an integrated plot with both boxplot and density plot for Jaccard_Index
IoU.perField.perROI.df.plot <- IoU.perField.perROI.df%>%
  filter(Jaccard_Index != 0)%>%
  ggplot(aes(x = Jaccard_Index,
             fill = ExpID)) +
  geom_boxplot(aes(y = 18), alpha = 0.5, outlier.shape = NA) + # Boxplot without outliers
  geom_jitter(aes(y = 18), width = 0.1, color = "black", alpha = 0.2,shape = 20 , size = 1) + # Jittered points inside the boxplot
  geom_density(aes(y = ..density..), fill = "black", alpha = 0.5) + # Density plot
  theme_prism(base_line_size = 8/14) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) + # Set x-axis from 0 to 1 with 0.1 intervals
  labs(title = "Jaccard Index per Field per Frame ROI",
       x = "IoU",
       y = "Frequency")
# Save the plot as a PDF
ggsave(paste(info.resDir ,"/Jaccard_Index_perField_perFrame_ROI_Plot.pdf",sep=""), plot = IoU.perField.perROI.df.plot   , width = 8, height = 6, device = "pdf")

```


### 3.2 ROI per Frame per Field lab meeting

```{r}
# Load necessary libraries
#install.packages("paletteer")

library(paletteer) # To use the color palette

# Create an integrated plot with both boxplot and density plot for Jaccard_Index
IoU.perField.perROI.df.LabMeeting.plot <- IoU.perField.perROI.df %>%
  filter(Jaccard_Index != 0) %>%
  ggplot(aes(x = Jaccard_Index)) +
  
  # Boxplot without outliers
  geom_boxplot(aes(y = 18), alpha = 0.5, outlier.shape = NA) +
  
  # Jittered points inside the boxplot, colored by timestep
  geom_jitter(aes(y = 18, 
                  fill = as.factor(timestep)), 
              width = 0.1,
              color = "black", 
              alpha = 0.7,
              shape = 21, 
              size = 0.2) +
  
  # Density plot
  geom_density(aes(y = ..density..),
               fill = "black", 
               alpha = 0.25) +
  
  # Manually define the color palette from colorBlindness::Blue2Orange12Steps, using only 4 colors
  scale_fill_manual(values = paletteer_d("colorBlindness::Blue2Orange12Steps")[c(1, 4, 8, 12)]) +
  
  # Customize axis and labels
  theme_prism(base_line_size = 8/14) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) + # Set x-axis from 0 to 1 with 0.1 intervals
  
  # Titles and labels
  labs(title = "Jaccard Index per Field per Frame ROI",
       x = "IoU",
       y = "Frequency",
       fill = "Timestep")

IoU.perField.perROI.df.LabMeeting.plot
```


```{r}
# Save the plot as a PDF
ggsave(paste(info.resDir ,"/Jaccard_Index_perField_perFrame_ROI_Plot.pdf",sep=""), plot = IoU.perField.perROI.df.plot   , width = 8, height = 6, device = "pdf")

```


```{r}
ROI.facet.AllData.df <- IoU.perField.perROI.df %>%
  mutate(Data = "0-72h")%>%
  select(-timestep)


ROI.facet.0hData.df <- IoU.perField.perROI.df %>%
  filter(timestep == "1")%>%
  mutate(Data = "0h")%>%
  select(-timestep)



ROI.facet.24hData.df <- IoU.perField.perROI.df %>%
  filter(timestep == "2")%>%
  mutate(Data = "24h")%>%
  select(-timestep)




ROI.facet.48hData.df <- IoU.perField.perROI.df %>%
  filter(timestep == "3")%>%
  mutate(Data = "48h")%>%
  select(-timestep)

ROI.facet.72hData.df <- IoU.perField.perROI.df %>%
  filter(timestep == "4")%>%
  mutate(Data = "72h")%>%
  select(-timestep)


ROI.facet.AllData.df <- rbind(ROI.facet.AllData.df,
                              ROI.facet.0hData.df)

ROI.facet.AllData.df <- rbind(ROI.facet.AllData.df,
                              ROI.facet.24hData.df)


ROI.facet.AllData.df <- rbind(ROI.facet.AllData.df,
                              ROI.facet.48hData.df)

ROI.facet.AllData.df <- rbind(ROI.facet.AllData.df,
                              ROI.facet.72hData.df)

rm(ROI.facet.0hData.df,
   ROI.facet.24hData.df,
   ROI.facet.48hData.df,
   ROI.facet.72hData.df)
```



```{r}
# Ensure 'Data' is a factor with the desired levels
ROI.facet.AllData.df.PLOT  <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0) %>%
  mutate(Data = factor(Data, levels = c("0h", "24h", "48h", "72h", "0-72h")))

# Create the violin plot with specific colors for each Data category
ROI.facet.AllData.df.PLOT <-ggplot(ROI.facet.AllData.df.PLOT, 
                                   aes(x = Data,
                                       y = Jaccard_Index)) +
  
  geom_hline(yintercept = 0.8, linetype = "dashed", color = "black", alpha = 0.2) +

  # Violin plots with specific colors
  geom_violin(aes(fill = Data), alpha = 0.7) +
  
  # Add boxplot inside the violin plot with light grey color
  geom_boxplot(width = 0.05, fill = "lightgrey", outlier.shape = NA, alpha = 0.8) +
  
  # Set y-axis limits from 0 to 1 with breaks at 0.2 intervals
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.2)) +
  
  # Manually set violin plot colors for each Data category
  scale_fill_manual(values = c("0h" = "#CCFFFF",
                               "24h" = "#99FFFF",
                               "48h" = "#66E5FF",
                               "72h" = "#0099CC",
                               "0-72h" = "black")) +
  
  # Customize the plot with labels and themes
  labs(title = "Violin Plot of Jaccard Index of ROIs",
       x = "",
       y = "IoU") +
  
  # Modify the theme to remove x-axis ticks and labels
  theme_prism(base_line_size = 8/14) +
  theme(axis.text.x = element_blank(),   # Remove x-axis text/labels
        axis.ticks.x = element_blank())  # Remove x-axis ticks


# Save the plot as a PDF
ggsave(paste(info.resDir ,"/Jaccard_Index_perField_perFrame_ROI_Plot.pdf",sep=""),
       plot = ROI.facet.AllData.df.PLOT   ,
       width = 8,
       height = 6,
       device = "pdf")
```

# Overall numbers for anaylsis
```{r}

#-- All data 
Info.Tot.N.of.ROIs.0.72h <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "0-72h")

Info.Tot.N.of.ROIs.0.72h  <- nrow(Info.Tot.N.of.ROIs.0.72h )
print(Info.Tot.N.of.ROIs.0.72h)


Info.Tot.N.of.ROIs.0.72h.stats <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "0-72h")%>%
  mutate(Mean.Roi = round(mean(Jaccard_Index), digits = 3),
         Median.Roi = median(Jaccard_Index))%>%
  mutate(Stat.mean.median = paste("IoU mean: ", Mean.Roi, " median: ",Median.Roi,sep=""))%>%
  select(Stat.mean.median)%>%
  distinct()

#-- 0h data 
Info.Tot.N.of.ROIs.0h <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "0h")


Info.Tot.N.of.ROIs.0h <- nrow(Info.Tot.N.of.ROIs.0h)
print(Info.Tot.N.of.ROIs.0h)

Info.Tot.N.of.ROIs.0h.stats <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "0h")%>%
  mutate(Mean.Roi = round(mean(Jaccard_Index), digits = 3),
         Median.Roi = median(Jaccard_Index))%>%
  mutate(Stat.mean.median = paste("IoU mean: ", Mean.Roi, " median: ",Median.Roi,sep=""))%>%
  select(Stat.mean.median)%>%
  distinct()


#-- 24h data 
Info.Tot.N.of.ROIs.24h <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "24h")

Info.Tot.N.of.ROIs.24h <- nrow(Info.Tot.N.of.ROIs.24h)

print(Info.Tot.N.of.ROIs.24h )

Info.Tot.N.of.ROIs.24h.stats <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "24h")%>%
  mutate(Mean.Roi = round(mean(Jaccard_Index), digits = 3),
         Median.Roi = median(Jaccard_Index))%>%
  mutate(Stat.mean.median = paste("IoU mean: ", Mean.Roi, " median: ",Median.Roi,sep=""))%>%
  select(Stat.mean.median)%>%
  distinct()


#-- 48h data 
Info.Tot.N.of.ROIs.48h <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "48h")

Info.Tot.N.of.ROIs.48h <-nrow(Info.Tot.N.of.ROIs.48h )

Info.Tot.N.of.ROIs.48h.stats <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "48h")%>%
  mutate(Mean.Roi = round(mean(Jaccard_Index), digits = 3),
         Median.Roi = median(Jaccard_Index))%>%
  mutate(Stat.mean.median = paste("IoU mean: ", Mean.Roi, " median: ",Median.Roi,sep=""))%>%
  select(Stat.mean.median)%>%
  distinct()


#-- 72h data 
Info.Tot.N.of.ROIs.72h <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "72h")


Info.Tot.N.of.ROIs.72h <- nrow(Info.Tot.N.of.ROIs.72h)

Info.Tot.N.of.ROIs.72h.stats <- ROI.facet.AllData.df %>%
  filter(Jaccard_Index != 0)%>%
  filter(Data == "72h")%>%
  mutate(Mean.Roi = round(mean(Jaccard_Index), digits = 3),
         Median.Roi = median(Jaccard_Index))%>%
  mutate(Stat.mean.median = paste("IoU mean: ", Mean.Roi, " median: ",Median.Roi,sep=""))%>%
  select(Stat.mean.median)%>%
  distinct()
```

## Export text file with numbers 
```{r}

# Define additional text
additional_text <- c(
  "Figure S1. Antimicrobial Single-Cell Testing (A)",
  "-------------------------------------",
  "Figure S1. Antimicrobial Single-Cell Testing.
(A) Overlay of “ground truth” bacterial segmentation with automated object segmentation (pixel classification) of M. abscessus brightfield images. The Jaccard index quantifies overlay accuracy across imaging frames during time-lapse acquisition.",
  "-----",
  "1. Information:",  # Adding a new line
  "Image data:",

  paste(unique(IoU.perField.perROI.df$ExpID),sep=""),
  paste("T10 & V10: Amikicin (AMK) treatment"),
  paste("S20: linezolid (LZD) treatment"),
  "Eeach image; 4 frames corresponding to: 0, 24, 48 and 72h timepoints",
  "",
  "-----",
  "ROI Jaccard index analysis:",
  "2. Number of ROIs",
  paste("At time 0h:", Info.Tot.N.of.ROIs.0h),
  paste("At time 24h:", Info.Tot.N.of.ROIs.24h),
  paste("At time 48h:", Info.Tot.N.of.ROIs.48h),
  paste("At time 72h:", Info.Tot.N.of.ROIs.72h),
  paste("At time 0-72h:", Info.Tot.N.of.ROIs.0.72h),

  "-----",
 "3. Mean & median IoU score:",
  paste("At time 0h:", Info.Tot.N.of.ROIs.0h.stats$Stat.mean.median),
  paste("At time 24h:", Info.Tot.N.of.ROIs.24h.stats$Stat.mean.median),
  paste("At time 48h:", Info.Tot.N.of.ROIs.48h.stats$Stat.mean.median),
  paste("At time 72h:", Info.Tot.N.of.ROIs.72h.stats$Stat.mean.median),
  paste("At time 0-72h:", Info.Tot.N.of.ROIs.0.72h.stats$Stat.mean.median),
  "-----"

)


# Combine additional text with the confusion matrix output and statistics
output_text <- c(
  additional_text)

today <- format(Sys.Date(), "%Y%m%d")

res.txt <- paste(info.resDir,
                       "/",
                       "ASCTsupp.Fig1a_Seg.Eval.IoU_",
                       today ,
                       ".txt",sep="")
# Write the combined text to a text file
writeLines(output_text,res.txt)



```

