---
title: "ASCT_Val3.4_Segmentation"
output: html_document
date: "2024-08-02"
---
# ================================================================
# Aim
# ================================================================
# Demonstrate that BaSiC flat-field/background correction:
# (i) removes frame-dependent fluorescence noise and
# (ii) aligns the trough (mode) of the PI intensity distributions
#     across timepoints in time-lapse images.

# Functionality:
# - Loads matched PI fluorescence tables (corrected & uncorrected)
#   and corresponding BF segmentation for object IDs.
# - Reshapes to long format and compares per-object intensity
#   distributions over timesteps.
# - Plots log10-intensity density curves ± peak locations for
#   corrected vs uncorrected data to visualise alignment over time.

# 1. Define variables
```{r}


info.wdDir <- getwd()
info.resDir <- paste(info.wdDir,
                     "/Fig_Results",
                     sep ="")

#---- Path to ASCT FLuncorr data
  ## Go back one level from the current working directory
  setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("FLcorr_H5")

  ## Get the current working directory
  info.FLcorrDir <- getwd()
  setwd(  info.FLcorrDir)
  
  
#---- Path to FLcorr data
 setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("FLuncorr_H5")
  
    info.FLuncorrDir <- getwd()
    setwd(    info.FLuncorrDir)
    
    
  
#---- Path to MOC data
 setwd("..")

  ## Change to the ASCT_nd2_images/ASCT_FL_images directory
  setwd("BF_H5")
  
    info.MOCDir <- getwd()
    setwd(    info.MOCDir)

```

# 2. load libraries
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)


library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)
library(stringr)

library(ggExtra)

library(wesanderson)


library(grid)  # Load the grid package allows you to add text to pages in ggplot

# For classification assement
library(caret)
```

# 3. Load data
## 3.1 FL corrected data
```{r}
FLcorr.df <- data.frame()

  

  # List all files in the current directory
    files <- list.files(info.FLcorrDir)
    
    # Filter files that end with 'ASCTassociation.csv'
    csv_files <- files[grep("_FLcorr_table.csv$", files)]
  # Loop through each of the CSV files and read them
  for (csv_file in csv_files) {
    
      setwd(info.FLcorrDir)
    # Read the CSV file
    FLcorr.df.sub <- read.csv(csv_file)
     FLcorr.df.sub <- FLcorr.df.sub %>%
       mutate(ExpID = csv_file)
    # Combine the data from the CSV file with the main data frame
    FLcorr.df <- rbind(FLcorr.df, FLcorr.df.sub)
  
  rm(FLcorr.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       csv_files)

FLcorr.df <- FLcorr.df %>%
  mutate(ExpID = gsub("_FLcorr_table.csv","",ExpID),
         ExpID = gsub("POC-","", ExpID))%>%
  mutate(Mean.Intensity.FLcorr = Mean.Intensity)%>%
  
  select(ExpID,
    labelimage_oid,
         
         timestep,
   Mean.Intensity.FLcorr,
          Center.of.the.object_1,
          Center.of.the.object_0)
```

## 3.2 FL uncorrected data
```{r}
FLuncorr.df <- data.frame()

  
  setwd(info.FLuncorrDir)
  # List all files in the current directory
    files <- list.files(info.FLuncorrDir)
    
    # Filter files that end with 'ASCTassociation.csv'
    csv_files <- files[grep("_FLuncorr_table.csv$", files)]
  
  # Loop through each of the CSV files and read them
  for (csv_file in csv_files) {
    # Read the CSV file
    FLuncorr.df.sub <- read.csv(csv_file)
        FLuncorr.df.sub <-FLuncorr.df.sub %>%
      mutate(ExpID = csv_file)
    
    # Combine the data from the CSV file with the main data frame
    FLuncorr.df <- rbind(FLuncorr.df, FLuncorr.df.sub)
  
  rm(FLuncorr.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       csv_files)

FLuncorr.df <- FLuncorr.df %>%
    mutate(ExpID = gsub("_FLuncorr_table.csv","",ExpID),
         ExpID = gsub("POC-","", ExpID))%>%
  mutate(Mean.Intensity.FLuncorr = Mean.Intensity)%>%
  select(ExpID,
         labelimage_oid,
         timestep,
         Mean.Intensity.FLuncorr,
        Center.of.the.object_1,
         Center.of.the.object_0)
```

## 3.3  MOC data
```{r}

MOC.df <- data.frame()

  
  setwd(info.MOCDir)
  # List all files in the current directory
    files <- list.files(info.MOCDir)
    
    # Filter files that end with 'ASCTassociation.csv'
    csv_files <- files[grep("_BF_ASCT_table.csv$", files)]
  
  # Loop through each of the CSV files and read them
  for (csv_file in csv_files) {
    # Read the CSV file
    MOC.df.sub <- read.csv(csv_file)
        MOC.df.sub <-MOC.df.sub %>%
      mutate(ExpID = csv_file)
    
    # Combine the data from the CSV file with the main data frame
    MOC.df <- rbind(MOC.df, MOC.df.sub)
  
  rm(MOC.df.sub)
  
  }

#Houskeeping
    rm(csv_file,
       csv_files)

MOC.df <- MOC.df %>%
    mutate(ExpID =gsub("_BF_ASCT_table.csv","",ExpID),
         ExpID = gsub("MOC-","", ExpID))%>%
  select(ExpID,
         labelimage_oid,
         timestep,
         Predicted.Class,
        Center.of.the.object_1,
         Center.of.the.object_0)
```

# 4. Merge data
```{r}
#Joining with `by = join_by(timestep, labelimage_oid, Center.of.the.object_0, Center.of.the.object_1, Field, Exp, Well_coordinate)`

Main.df <- left_join(FLcorr.df,
                     FLuncorr.df,
                     by = c("ExpID",
                            "labelimage_oid",
                            "timestep",
                           "Center.of.the.object_1",
                            "Center.of.the.object_0"
                            ))


Main.df <- Main.df %>%
  drop_na()


Main.df <- left_join(Main.df,
                     MOC.df)

rm(FLcorr.df,
   FLuncorr.df,
   MOC.df)
```


```{r}
Main.df <- Main.df %>%
  select(ExpID,
         labelimage_oid,
         timestep,
         Center.of.the.object_1,
         Center.of.the.object_0,
         Mean.Intensity.FLuncorr,
         Mean.Intensity.FLcorr)
```



```{r}
str(Main.df)


Main.df <- Main.df%>%
  pivot_longer(cols = c(Mean.Intensity.FLuncorr, Mean.Intensity.FLcorr),
               names_to = "Correction",
               values_to = "Intensity_Value")


str(Main.df )

Main.df <- Main.df %>%
  mutate(timestep =as.numeric(timestep))%>%
 mutate(Correction = factor(if_else(Correction == "Mean.Intensity.FLuncorr", 
                                     "Uncorrected", 
                                     "BaSic corrected"),
                             levels = c("Uncorrected", "BaSic corrected")))
```




```{r}


color_palette <- wes_palette("Zissou1", 30, type = "continuous")


# Create the density plot
Main.df %>%
 # filter(ExpID == "ASCTmut.03.20240522_I10_p05")%>%
ggplot( aes(x = log10(Intensity_Value), color = factor(timestep), fill = factor(timestep))) +
  geom_density(alpha = 1, fill = NA) +  # Set fill to NA to remove fill color
  scale_color_manual(values = color_palette) +
  scale_fill_manual(values = color_palette) +

  labs(title = "Density Plot of PI singal intensity",
       x = " Log10 fluorescence intensity",
       y = "Density",
       color = "Timestep",
       fill = "Timestep") +
  theme_prism(base_line_size = 8/14)+
  theme(legend.text = element_text(size = 8),    # Adjust the size of the legend text
        legend.title = element_text(size = 9),   # Adjust the size of the legend title (if needed)
        legend.key.size = unit(0.5, "cm"))    +   # Adjust the size of the legend key
    facet_wrap(~ Correction) 


# Save the plot as a PDF in the Fig_Results directory
ggsave(filename = "Fig_Results/ASCTsupp_Background.correction_Density.plot.pdf", 
       plot = last_plot(), # Saves the last ggplot created
       device = "pdf",
       width = 10, height = 7) # Adjust width and height as needed

```

