
# ================================================================
# Aim
# ================================================================
# Compare 7-day time-kill kinetics of M. tuberculosis under standard
# treatment regimens across multiple drug combinations, experiments and
# physiological states.
#
# This script:
# - Loads Trkv2_LCF tracking outputs and corresponding raw killing features
#   (_Trkv2_rawKF, via KFintermediary) for all ASCT MTB experiments in
#   ASCT_Data.
# - Filters wells based on QC flags (Overall.Assessment and Multiple.Events)
#   and reconstructs time-kill curves, appending the endpoint (168 h) LCF.
# - Aggregates mean live-cell fractions per drug–isolate–timepoint and
#   standardises experiment IDs and isolate annotations (e.g. H37Ra vs
#   PBS-starved H37Ra).
# - For each isolate and experiment, computes how many of the tested drugs
#   are represented (N.drugs.per.Exp) to track treatment coverage.
# - Generates mean time-kill plots:
#     (i) per experiment (ASCT.09 / ASCT.10) with drug-specific colors,
#     (ii) focused on H37Ra vs PBS-starved H37Ra under standard treatment,
#   with linear [% alive] readouts over 0–168 h.
# - Exports publication-ready PDFs of mean time-kill curves with consistent
#   color coding for first-line and novel regimens.

# Section 1: Defining variables
```{r setup, include=FALSE}

genDir <- getwd() 


#Pop data variables
data.dir <- c("ASCT_Data")
res.dir <- c("Experimental-Results")

type.of.analysis <- c("Wellbased.Fitting")

exp.res.dir <- c(paste(genDir,
                       "/",
                       "Experimental-Results",sep=""))
wdDir <- genDir

res.dir <- paste(genDir,"/",res.dir ,sep="")

data.dir <- paste(genDir,
                  "/",
                  data.dir,
                  sep="")
setwd(wdDir)

# list the experiment directories to pull the tracking data


# EDIT the time scale axis that should be used 
plot.xaxis.time.scale <- c(0,  24,  48, 72,  96,  120,  144,  168)






```

# Section 2: Loading packages
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels) 
library(MESS)
library(gghighlight)
library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)

```

## 2.1 Loop through Experimental Results
```{r}

Main.Tracking.df <- data.frame()

Main.KF.df <- data.frame()

# Load KF.intermediary table
KFinter.files <- list.files(data.dir, pattern = "_Trkv2_KFintermediary.csv", full.names = TRUE)
i <- KFinter.files[1]
for ( i in     KFinter.files ) {
    
  
  KF.intermediary.df <- read.csv(i)
    print(i)
         KF.intermediary.df <-   KF.intermediary.df %>%
           filter(Merge.def == "Trkv2_Ila2BaSic")%>%
           select(ExpFile,
                  Abx.con,
                  Well_coordinate,
                  Multiple.Events)%>%
           distinct()

         x <- sub(
                  "_Trkv2_KFintermediary.csv$",
                  "_Trkv2_LCF_flags.csv",i)
    
  # Load Trkv2 Flags

  Tracking.df <- read.csv(   x )
  
    Tracking.df <-   Tracking.df %>%
      filter(Time.Kill.Definitions == "Trkv2_LCF_Ila2BaSic")%>%
      left_join(         KF.intermediary.df )
    
    
    Main.Tracking.df <- rbind(    Main.Tracking.df,
                                     Tracking.df )
    
    

 x <- sub(
              
                  "_Trkv2_LCF_flags.csv$",
                   "_Trkv2_rawKF.csv",
                  i)
        
    KFraw <- read.csv(   x )
    
    KFraw <-KFraw %>%
      filter(Killing.Def == "Trkv2_LCF_Ila2BaSic")
    
    
    Main.KF.df <- rbind(    Main.KF.df ,   KFraw )
    

    }
    


  rm(KF.intermediary.df,
     KFraw,
     Tracking.df)

```



```{r}
# ---

Main.KF.df <- Main.KF.df %>%
  mutate(Killing.Def = gsub("Trkv2_LCF_Ila2BaSic","Trkv2_Ila2BaSic", Killing.Def))
  

Main.KF.df <- Main.KF.df %>%
  mutate(Sub.KF = Killing.Features)%>%
  mutate(Sub.KF = gsub("Trkv2_LCF_","",Sub.KF))%>%
    mutate(Sub.KF= gsub("_Ila2BaSic", "",Sub.KF))%>%
  mutate(Time_Hrs = gsub("h","",Sub.KF)) %>%
  mutate(Time_Hrs = as.numeric(Time_Hrs))%>%
  mutate(Time.Kill.Definitions = Killing.Def)%>%
  mutate(LC.fraction.corr = value)%>%
  mutate(ExpFile.Wellcoordinate = paste(ExpFile,
                                        Well_coordinate,
                                        sep="_"))%>%
  select(ExpFile,
         Abx.con,
         Isolate,
         ExpFile.Wellcoordinate ,
         Well_coordinate,
         Time_Hrs,
         Time.Kill.Definitions ,
         LC.fraction.corr)%>%
  distinct()%>%
  filter(Time_Hrs == max(plot.xaxis.time.scale)) # KEEPING ONLY 168h KF
  
  


# ---
Main.Tracking.df <- Main.Tracking.df %>%
  ungroup()%>%
  filter(Overall.Assessment == "Keep" &
           Multiple.Events == "Keep")


Main.Tracking.df <- Main.Tracking.df %>%
  mutate(ExpFile.Wellcoordinate = paste(ExpFile,
                                        Well_coordinate,
                                        sep="_"))#%>%
  # select(-Overall.Assessment,
  #        -Multiple.Events,
  #        -Flag.label)


Main.Tracking.df <- Main.Tracking.df %>%
mutate(timestep = as.numeric(timestep))


list.of.Well.coordinates.Kept.in.analysis <- unique(Main.Tracking.df$ExpFile.Wellcoordinate)

Main.KF.df <- Main.KF.df %>%
  filter(ExpFile.Wellcoordinate %in% list.of.Well.coordinates.Kept.in.analysis)

Main.KF.df <- Main.KF.df %>%
  mutate(timestep = as.numeric(max(Main.Tracking.df$timestep)+1))

# Assume your y-axis linear scale values range from 1 to 100%

linear_breaks <- c( 40,50,60 ,70,80,90, 100) # Modify this based on your data

# Convert these to log10 scale for the breaks
log_breaks <- log10(linear_breaks)

Main.Tracking.df <- Main.Tracking.df %>%
  mutate(ExpID =paste("ASCT.",
                      gsub("^.*\\.(.*)\\..*$", "\\1", ExpFile),
                      sep=""))

Main.KF.df  <- Main.KF.df %>%
  mutate(ExpID =paste("ASCT.",
                      gsub("^.*\\.(.*)\\..*$", "\\1", ExpFile),
                      sep=""))


```

# Merging Killing Features and Main tracking Data 
```{r}

Exp.QC <- Main.Tracking.df %>%
  select(ExpFile,
         Well_coordinate,
         Flag.label,
         Overall.Assessment,
         Multiple.Events)%>%
  distinct()
  

variable_names <- names(Main.KF.df)

Main.Tracking.df <- Main.Tracking.df %>%
   select(all_of(variable_names))

Main.KF.df  <- Main.KF.df %>%
  mutate(Time.Kill.Definitions = if_else(Time.Kill.Definitions == "Trkv2_Ila2BaSic", "Trkv2_LCF_Ilas2BaSic", Time.Kill.Definitions))
  
Main.Tracking.df <- rbind(Main.Tracking.df,
                          Main.KF.df)

Main.Tracking.df <- Main.Tracking.df %>%
  left_join(Exp.QC)


rm(Exp.QC)



```






```{r}
library(stringr)
Main.Mean.Tracking.df<- Main.Tracking.df %>%

  group_by(#ExpFile,
           Abx.con,
           Isolate,
           timestep)%>%
mutate(Mean.LC.fraction.corr = mean(LC.fraction.corr),
         Mean.Time_Hrs = mean(Time_Hrs))%>%
  ungroup()%>%
  filter(Time_Hrs <= max(plot.xaxis.time.scale))%>%
  select(ExpID,
         Time.Kill.Definitions,
         Abx.con,
         Isolate,   
         Mean.Time_Hrs,
         Mean.LC.fraction.corr)%>%
  distinct()%>%
  mutate(Drug=   sub("_.*", "", Abx.con)  )%>%
  mutate(Isolate = gsub("7h9","pan",Isolate))%>%
  mutate(Isolate = gsub("log","",Isolate))%>%
  mutate(Type.of.Analysis = type.of.analysis)%>%
  filter(!Drug %in% c("Ka", "Kb", "Kc", "NodDrug"))%>%
  filter(Isolate != "Iso.Hipos")
```


```{r}
#----------

N.drugs.In.exp <- Main.Mean.Tracking.df %>%
  select(Drug)%>%
  distinct()
 
N.drugs.In.exp<-   nrow(N.drugs.In.exp)



Conditions.df.Drugs.perExp <- Main.Mean.Tracking.df %>%
  select(ExpID,
         Drug,
         Isolate)%>%
  distinct()%>%
  group_by(ExpID,
           Isolate)%>%
  mutate(N.Drugs.per.Exp =1,
         N.Drugs.per.Exp = sum(N.Drugs.per.Exp ))%>%
  ungroup()%>%
  mutate(        N.Drugs.per.Exp = paste(N.Drugs.per.Exp,
                                  "/",
                                N.drugs.In.exp ,
                                  sep=""))%>%
  ungroup()%>%
  select(ExpID,
          Isolate,
          N.Drugs.per.Exp)%>%
  distinct()


Main.Mean.Tracking.df <- left_join(Main.Mean.Tracking.df ,
                           Conditions.df.Drugs.perExp)


Main.Mean.Tracking.df <- Main.Mean.Tracking.df %>%
 mutate(N.Drugs.per.Exp = paste("N.drugs: ",
                                 N.Drugs.per.Exp,
                                 sep=""))



rm(N.drugs.In.exp,
   Conditions.df.Drugs.perExp)


x <- unique(Main.Mean.Tracking.df$Abx.con)
```


```{r}

plot.filename <- paste(exp.res.dir,"/ASCTmtb_Mean_TimeKillcurve_7dayExp_",type.of.analysis ,"_MTBmc2700.H37Ra-notStarved_StandardTreatment.pdf", sep = "")


#--- Y axis ticks
linear_breaks <- c(0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.0) # Modify this based on your data

# Convert these to log10 scale for the breaks
log_breaks <- log10(linear_breaks)

linear_breaks.label <- c(40, 50, 60, 70, 80, 90, 100)
#---

# Set colors based on the drug names
Main.Mean.Tracking.df <- Main.Mean.Tracking.df %>%
  mutate(color = case_when(
    Drug == "EHRZ" ~ "darkblue",
    Drug == "HR" ~ "steelblue",
    Drug == "BLPa" ~ "red",
    Drug == "BPaZ" ~ "purple",
    
    grepl("H|R|E", Drug) ~"darkgreen",
    TRUE ~ "black"
  ))



library(ggrepel)
gg <- Main.Mean.Tracking.df %>%
  mutate(Mean.LC.fraction.corr = Mean.LC.fraction.corr * 100) %>%
  filter(Mean.Time_Hrs <= max(plot.xaxis.time.scale)) %>%
  filter(ExpID %in% c("ASCT.09", "ASCT.10"))%>%
  ungroup() %>%
  ggplot(aes(x = Mean.Time_Hrs,
             y = Mean.LC.fraction.corr,
             group = Drug,
             label = Drug,
             colour = color)) +  # Use the color column for colors
  geom_line(alpha = 0.50, 
            size = 0.2, 
            stroke = 0) +
  scale_colour_identity() +  # Use the colors as defined
  theme_prism(base_line_size = 0.2) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100),
                     limits = c(0, 100),
                     labels = c(0, 20, 20, 60, 80, 100)) +
  theme(axis.text = element_text(size = 7)) +
  theme(strip.text.x = element_text(size = 7)) +
  theme(legend.key.size = unit(0.1, "cm"),
        legend.key.width = unit(0.1, "cm")) +
  scale_x_continuous(breaks = plot.xaxis.time.scale) +
  labs(
       subtitle = "linear scale",
       x = "Time [Hrs]",
       y = "Percent of cells alive [%]",
       color = "Drugs",
       caption = "Color scheme: EHRZ = dark blue,\nHR = steel blue,\nBLPa = red,\nH/R/E = dark green,\nBpaZ = purple,\nOthers = black.") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1) +
  theme(plot.subtitle = element_text(size = 7)) +
  theme(legend.position = "none") +  # Removes the legend
  facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 3,
                      nrow = 1,
                      page = 1)

n <- n_pages(gg)

pdf(plot.filename, paper = "a4", width = 20, height = 15)
for(i in 1:n){
    print(gg + facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 3,
                      nrow = 1, page = i)) 
}
dev.off()

# Housekeeping
rm(gg, plot.filename, g)


```


```{r}

plot.filename <- paste(exp.res.dir,"/ASCTmtb_Mean_TimeKillcurve_7dayExp_",type.of.analysis ,"_MTB_H37Ra_StandardTreatment.pdf", sep = "")


#--- Y axis ticks
linear_breaks <- c(0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.0) # Modify this based on your data

# Convert these to log10 scale for the breaks
log_breaks <- log10(linear_breaks)

linear_breaks.label <- c(40, 50, 60, 70, 80, 90, 100)
#---

# Set colors based on the drug names
Main.Mean.Tracking.df <- Main.Mean.Tracking.df %>%
  mutate(color = case_when(
    Drug == "EHRZ" ~ "darkblue",
    Drug == "HR" ~ "steelblue",
    Drug == "BLPa" ~ "red",
    Drug == "BPaZ" ~ "purple",
    
    grepl("H|R|E", Drug) ~"darkgreen",
    TRUE ~ "black"
  ))



library(ggrepel)
gg <- Main.Mean.Tracking.df %>%
  mutate(Mean.LC.fraction.corr = Mean.LC.fraction.corr * 100) %>%
  filter(Mean.Time_Hrs <= max(plot.xaxis.time.scale)) %>%
# filter(ExpID == "ASCT.09" & ExpID =="ASCT.07" )%>%
  filter(Isolate == "Iso.H37Ra" | Isolate == "Iso.H37RapbsStrvd" )%>%
  
  ungroup() %>%
  ggplot(aes(x = Mean.Time_Hrs,
             y = Mean.LC.fraction.corr,
             group = Drug,
             label = Drug,
             colour = color)) +  # Use the color column for colors
  geom_line(alpha = 0.50, 
            size = 0.2, 
            stroke = 0) +
  scale_colour_identity() +  # Use the colors as defined
  theme_prism(base_line_size = 0.2) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100),
                     limits = c(0, 100),
                     labels = c(0, 20, 20, 60, 80, 100)) +
  theme(axis.text = element_text(size = 7)) +
  theme(strip.text.x = element_text(size = 7)) +
  theme(legend.key.size = unit(0.1, "cm"),
        legend.key.width = unit(0.1, "cm")) +
  scale_x_continuous(breaks = plot.xaxis.time.scale) +
  labs(
       subtitle = "linear scale",
       x = "Time [Hrs]",
       y = "Percent of cells alive [%]",
       color = "Drugs",
       caption = "Color scheme: EHRZ = dark blue,\nHR = steel blue,\nBLPa = red,\nH/R/E = dark green,\nBpaZ = purple,\nOthers = black.") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1) +
  theme(plot.subtitle = element_text(size = 7)) +
  theme(legend.position = "none") +  # Removes the legend
  facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 2,
                      nrow = 1,
                      page = 1)

n <- n_pages(gg)

pdf(plot.filename, paper = "a4", width = 20, height = 15)
for(i in 1:n){
    print(gg + facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 2,
                      nrow = 1, page = i)) 
}
dev.off()

# Housekeeping
rm(gg, plot.filename, g)
```

