---
title: "ASCTreporter PI_GFP"
author: "Alex"
date: "2025-07-29"
output: html_document
---

# ================================================================
# Aim
# ================================================================
# This script processes ASCT reporter data (GFP / PI channels) from
# GOC, MOC, and POC outputs to generate gated FACS-like plots across
# antibiotics and timepoints.
#
# Functions:
# - Load and merge GOC, MOC, and POC intensity + classification data.
# - Filter for single-cell objects (MOC = "SC").
# - Assign antibiotic conditions based on well coordinates.
# - Compute log-transformed PI and GFP intensities.
# - Derive gating thresholds (manual, mean–SD, GMM).
# - Classify cells into GFP+/− and PI+/− quadrants per method.
# - Count quadrant frequencies per antibiotic × timepoint.
# - Generate hex-density FACS plots with gating overlays and quadrant
#   percentages (Fig. 1F style).
#
# Output:
# - Gated FACS PDFs for each thresholding strategy.
# - Clean merged reporter dataset for downstream analysis.

# 1. load libraries
```{r}
library(tidyverse)
library(ggplot2)
library(data.table)
library(parallel)

```

# 2. Define paths
```{r}
info.wd <- getwd()
info.expID <- c("ASCTrep.01.20250722")
info.ASCTdir <- c("ASCT_data")

info.data.dir.GOC <-c("GOCcsv")
info.data.dir.MOC <-c("MOCcsv")
info.data.dir.POC <-c("POCcsv")


```

# Load GOC
```{r}
# Construct full path to the GOC CSV folder
data_path_GOC <- file.path(
  info.wd,
  info.ASCTdir,
  paste0(info.expID, "_", info.data.dir.GOC)
)

# List all CSV files
files <- list.files(data_path_GOC, pattern = "\\.csv$", full.names = TRUE)

# Combine all CSV files into one data frame
GOC.df <- do.call(rbind, lapply(files, function(f) {
  if (file.size(f) > 1) {         # only read if larger than 1 byte
    df <- read.csv(f, stringsAsFactors = FALSE)
    df$source_file <- basename(f)
    return(df)
  } else {
    message("Skipping empty file: ", f)
    return(NULL)
  }
}))

# Check dimensions and preview

GOC.df <- GOC.df %>%
  mutate(Predicted.Class.GOC = if_else(Predicted.Class == "piNEG", "-", "+"))%>%
    mutate( Mean.Intensity.GOC = Mean.Intensity)%>%

  select(source_file,
         timestep,
         Size.in.pixels,
         Center.of.the.object_0,
         Center.of.the.object_1,
         Predicted.Class.GOC,
Mean.Intensity.GOC)


```

# Load MOC
```{r}
# Construct full path to the MOC CSV folder
data_path_MOC <- file.path(
  info.wd,
  info.ASCTdir,
  paste0(info.expID, "_", info.data.dir.MOC)
)

# List all CSV files
files <- list.files(data_path_MOC, pattern = "\\.csv$", full.names = TRUE)

# Combine all CSV files into one data frame
MOC.df <- do.call(rbind, lapply(files, function(f) {
  if (file.size(f) > 1) {         # only read if larger than 1 byte
    df <- read.csv(f, stringsAsFactors = FALSE)
    df$source_file <- basename(f)
    return(df)
  } else {
    message("Skipping empty file: ", f)
    return(NULL)
  }
}))

# Check dimensions and preview

MOC.df <- MOC.df %>%
  mutate(Predicted.Class.MOC =     Predicted.Class)%>%
  select(source_file,
         timestep,
         Size.in.pixels,
         Center.of.the.object_0,
         Center.of.the.object_1,
         Predicted.Class.MOC)
```


```{r}
# Construct full path to the POC CSV folder
data_path_POC <- file.path(
  info.wd,
  info.ASCTdir,
  paste0(info.expID, "_", info.data.dir.POC)
)

# List all CSV files
files <- list.files(data_path_POC, pattern = "\\.csv$", full.names = TRUE)

# Combine all CSV files into one data frame
POC.df <- do.call(rbind, lapply(files, function(f) {
  if (file.size(f) > 1) {         # only read if larger than 1 byte
    df <- read.csv(f, stringsAsFactors = FALSE)
    df$source_file <- basename(f)
    return(df)
  } else {
    message("Skipping empty file: ", f)
    return(NULL)
  }
}))

# Check dimensions and preview

POC.df <- POC.df %>%
    mutate(Predicted.Class.POC = if_else(Predicted.Class == "piNEG", "-", "+"))%>%

    mutate(   Mean.Intensity.POC =     Mean.Intensity)%>%

  select(source_file,
         timestep,
         Size.in.pixels,
         Center.of.the.object_0,
         Center.of.the.object_1,
         Predicted.Class.POC,
         Mean.Intensity.POC)
```
# Merging data
```{r}
MOC.df <- MOC.df %>%
  mutate(Well_coordinate = sub("OCsimple_MOC_","", source_file))%>%
  mutate(Well_coordinate =sub(".csv","",Well_coordinate))%>%
  select(-source_file)

POC.df <- POC.df %>%
  mutate(Well_coordinate = sub("OCsimple_POCbSd_","", source_file))%>%
  mutate(Well_coordinate =sub(".csv","",Well_coordinate))%>%
  select(-source_file)

GOC.df <- GOC.df %>%
  mutate(Well_coordinate = sub("OCsimple_GOC_","", source_file))%>%
  mutate(Well_coordinate =sub(".csv","",Well_coordinate))%>%
  select(-source_file)
```

```{r}
ASCTrep.df <- left_join(MOC.df,
                        POC.df)

ASCTrep.df <- left_join(ASCTrep.df ,
                        GOC.df)

rm(MOC.df,
   POC.df,
   GOC.df)

ASCTrep.df <-ASCTrep.df %>%
  select(Well_coordinate,
         Center.of.the.object_0,
         Center.of.the.object_1,
         timestep,
         Size.in.pixels,
         Predicted.Class.MOC,

         Predicted.Class.POC,
         Mean.Intensity.POC,
                  Predicted.Class.GOC,
                  Mean.Intensity.GOC)
```

# Selecting MOC class 
```{r}
# FILTERING FOR SC only
ASCTrep.df <- ASCTrep.df %>%
  filter(Predicted.Class.MOC == "SC")
  #filter(Predicted.Class.MOC == "SC" | Predicted.Class.MOC == "VS")%>%
#  filter(Predicted.Class.MOC == "SC" | Predicted.Class.MOC == "VS" | Predicted.Class.MOC == "C2")


```
## Free unused memory
```{r}
gc()
```

```{r}
ASCTrep.df <- ASCTrep.df %>%
  separate(
    col = Well_coordinate,
    into = c("ExpID", "Well_coordinate", "Field"),
    sep = "_",
    remove = FALSE  # keep the original column
  )

#----
```


```{r}
ASCTrep.df <- ASCTrep.df %>%

  select(ExpID,
         Well_coordinate,
         Field,
         Center.of.the.object_0,
         Center.of.the.object_1,
         timestep,
         Size.in.pixels,
         Predicted.Class.MOC,
 Predicted.Class.POC,
         Mean.Intensity.POC,
                  Predicted.Class.GOC,
                  Mean.Intensity.GOC)%>%
  drop_na()


ASCTrep.df$class <- with(ASCTrep.df, paste0("GFP", Predicted.Class.GOC, "_PI", Predicted.Class.POC))
table(ASCTrep.df$class)


ASCTrep.df <- ASCTrep.df %>%
  mutate(
    Abx.con = case_when(
      Well_coordinate %in% c("B3","B4","B5") ~ "IPM",
      Well_coordinate %in% c("C3","C4","C5") ~ "FOX",
      Well_coordinate %in% c("D3","D4","D5") ~ "AMK",
      Well_coordinate %in% c("E3","E4","E5") ~ "TGC",
      Well_coordinate %in% c("F3","F4","F5") ~ "MIN",
      Well_coordinate %in% c("G3","G4","G5") ~ "AZM",
      Well_coordinate %in% c("H3","H4","H5") ~ "MXF",
      Well_coordinate %in% c("I3","I4","I5") ~ "LIN",
      Well_coordinate %in% c("J3","J4","J5") ~ "ATc",
      TRUE ~ NA_character_
    )
  )
```


```{r}
keep_abx <- c("ATc", "FOX",  "MXF", "AMK")

ASCTrep.df  <- ASCTrep.df %>%
 # filter(timestep %in% selected_tsteps) %>%
  mutate(timestep = timestep * 0.5)%>%
  filter(timestep <= 24)%>%
    mutate(timestep = if_else(timestep == 23.5, 24, timestep))%>%
 mutate(timestep = as.numeric(timestep))%>% # convert back to numeric
      filter(                     Abx.con %in% keep_abx)

ASCTrep.df<- ASCTrep.df %>%
  dplyr::filter(timestep %in% c(0, 2, 4, 6, 8, 10, 12))



library(dplyr)



```


# FACS like plots 
## FACS plots without gating
```{r}

library(ggplot2)
library(ggpubr)
library(wesanderson)
library(mclust)

# Subset controls
GFP_control <- subset(ASCTrep.df, Abx.con == "ATc" & Mean.Intensity.GOC > 0 & timestep == 0)
PI_control  <- subset(ASCTrep.df, Abx.con %in% c("ATc") & Mean.Intensity.POC > 0 & timestep == 0)

# Add log10-transformed intensity columns
GFP_control$Mean.Intensity.GOC.log10 <- log10(GFP_control$Mean.Intensity.GOC)
PI_control$Mean.Intensity.POC.log10 <- log10(PI_control$Mean.Intensity.POC)

manual_GFP_log <- 1.75
manual_PI_log  <- 1.75

# Mean ± 3SD thresholds
threshold_GFP_log_mean1sd <- mean(GFP_control$Mean.Intensity.GOC.log10, na.rm = TRUE) - sd(GFP_control$Mean.Intensity.GOC.log10, na.rm = TRUE)

threshold_PI_log_mean1sd <- mean(PI_control$Mean.Intensity.POC.log10, na.rm = TRUE) - sd(PI_control$Mean.Intensity.POC.log10, na.rm = TRUE)

# GMM thresholds (midpoint between means)


gmm_GFP <- Mclust(GFP_control$Mean.Intensity.GOC.log10, G = 2)
means_GFP <- sort(gmm_GFP$parameters$mean)
threshold_GFP_log_gmm <- mean(means_GFP)

# GMM on PI
gmm_PI <- Mclust(PI_control$Mean.Intensity.POC.log10, G = 2)
means_PI <- sort(gmm_PI$parameters$mean)
threshold_PI_log_gmm <- mean(means_PI)

```



```{r}
# 1. Add log10 columns to the full dataframe (if not already present)
ASCTrep.df$Mean.Intensity.POC.log10 <- log10(ASCTrep.df$Mean.Intensity.POC)
ASCTrep.df$Mean.Intensity.GOC.log10 <- log10(ASCTrep.df$Mean.Intensity.GOC)

# 2. Define a helper function for gating
gate_status <- function(log_gfp, log_pi, gfp_thresh, pi_thresh) {
  if (is.na(log_gfp) | is.na(log_pi)) return(NA)
  gfp_label <- ifelse(log_gfp > gfp_thresh, "GFP+", "GFP-")
  pi_label  <- ifelse(log_pi  > pi_thresh,  "PI+",  "PI-")
  return(paste(gfp_label, pi_label, sep = "_"))
}

# 3. Apply all three gating strategies

## Manual thresholds
ASCTrep.df$gate_manual <- mapply(
  gate_status,
  ASCTrep.df$Mean.Intensity.GOC.log10,
  ASCTrep.df$Mean.Intensity.POC.log10,
  manual_GFP_log,
  manual_PI_log
)

## Mean − 3SD thresholds
ASCTrep.df$gate_mean1sd <- mapply(
  gate_status,
  ASCTrep.df$Mean.Intensity.GOC.log10,
  ASCTrep.df$Mean.Intensity.POC.log10,
  threshold_GFP_log_mean1sd,
  threshold_PI_log_mean1sd
)

## GMM thresholds
ASCTrep.df$gate_gmm <- mapply(
  gate_status,
  ASCTrep.df$Mean.Intensity.GOC.log10,
  ASCTrep.df$Mean.Intensity.POC.log10,
  threshold_GFP_log_gmm,
  threshold_PI_log_gmm
)

ASCTrep.df <- ASCTrep.df %>%
  ungroup()%>%
  mutate(GMM.only = sub("_.*", "",gate_gmm))%>%
  mutate(gate_GMM.GFP_Ila.PI = paste(GMM.only,
                                "_",
                                "PI",
                                Predicted.Class.POC,
                                sep=""))


```


```{r}
# 1. Reshape to long format across all three gating strategies
df_long_all <- ASCTrep.df %>%
  select(Abx.con, timestep, gate_manual, gate_mean1sd, gate_gmm, gate_GMM.GFP_Ila.PI) %>%
  pivot_longer(
    cols = starts_with("gate_"),
    names_to = "strategy",
    names_prefix = "gate_",
    values_to = "category"
  ) %>%
  filter(!is.na(category))

# Zissou palette
zissou_cols <- wes_palette("Zissou1", type = "continuous")

# 2. Count cells per category × strategy × Abx × timestep
df_counts <- df_long_all %>%
  group_by(strategy, Abx.con, timestep, category) %>%
  summarise(count = n(), .groups = "drop")

# 3. Define quadrant position and labels
pos_map <- tibble(
  category = c("GFP+_PI+", "GFP+_PI-", "GFP-_PI+", "GFP-_PI-"),
  x = c(3.25, 0.2, 3.25, 0.2),
  y = c(3.25, 3.25, 0.2, 0.2),
  quad_label = c("PI+ GFP+", "PI- GFP+", "PI+ GFP-", "PI- GFP-")
)

# 4. Join labels and compute percentage and label text
df_counts <- df_counts %>%
  left_join(pos_map, by = "category") %>%
  group_by(strategy, Abx.con, timestep) %>%
  mutate(
    percent = 100 * count / sum(count),
    label_text = paste0(
      round(percent, 1), "%\n",
      count, "\n",
      quad_label
    )
  ) %>%
  ungroup()
```


```{r}

ASCTrep.df <- ASCTrep.df %>%
  mutate(Abx.con = ifelse(Abx.con == "ATc", "Control", Abx.con))

ASCTrep.df <- ASCTrep.df%>%
    filter(!(Abx.con == "Control" & timestep > 0))

  

df_counts <- df_counts %>%
    mutate(Abx.con = ifelse(Abx.con == "ATc", "Control", Abx.con))


df_counts <- df_counts %>%
  filter(!(Abx.con == "Control" & timestep > 0))

```

## Threshold strategies and counts per timepoint with percentages
```{r}

# Define parameters for each strategy
#strategies <- c("manual", "mean1sd", "gmm" , "GMM.GFP_Ila.PI")
strategies <- c( "gmm" )

#vlines <- c(manual_PI_log, threshold_PI_log_mean1sd, threshold_PI_log_gmm)
vlines <- c( threshold_PI_log_gmm)

#hlines <- c(manual_GFP_log, threshold_GFP_log_mean1sd, threshold_GFP_log_gmm)
hlines <- c( threshold_GFP_log_gmm)

#linetypes <- c("solid", "dotted", "dashed")

linetypes <- c( "dashed")



captions <- c("Thresholds shown: Dashed lines = Gaussian Mixture Model thresholds GFP intensity for GFP threshold\n PI intensity for PI thrs using ATc control at t0")



thresholds_list <- list(
 
  gmm = list(
    GFP = threshold_GFP_log_gmm,
    PI = threshold_PI_log_gmm
  )
  
)


# Loop through each strategy
for (i in seq_along(strategies)) {
  
  strategy <- strategies[i]
  str.filter <-  strategy 
  lt <- linetypes[i]
  caption_text <- captions[i]
  thrs <- thresholds_list[[strategy]]
  
  df_labels <- df_counts %>%
    filter(strategy ==  str.filter)%>%
    ungroup()%>%
    group_by(strategy,
             Abx.con,
             timestep)%>%
      mutate(
    label_text = paste0(
      round(percent, 1), "%\n",  # % at the top
      count, "\n"#,               # count in the middle
 #     quad_label                # label on the bottom (e.g., PI+ GFP+)
    )
  ) # 👈 REMOVE this column



  p <- ggplot(ASCTrep.df, aes(
    x = Mean.Intensity.POC.log10,
    y = Mean.Intensity.GOC.log10)) +
    geom_hex(bins = 100) +
    scale_fill_gradientn(
      colors = zissou_cols,
      trans = "log10",
      name = "Cell count"
    ) +
   # coord_cartesian(xlim = c(0, 3.75), ylim = c(0, 3.75)) +
    geom_vline(xintercept = thrs$PI, linetype = lt, color = "black", linewidth = 0.8) +
    geom_hline(yintercept = thrs$GFP, linetype = lt, color = "black", linewidth = 0.8) +

    # ✅ Clean quadrant labels at grid positions
geom_text(
  data = df_labels,
  aes(
    x = x,
    y = y,
    label = label_text,
    group = interaction(Abx.con, timestep )  # helps ensure grouping
  ),
  inherit.aes = FALSE,
  size = 4,
  lineheight = 0.9,
 # fontface = "bold",
  color = "black"
)+
    labs(
      x = "log10 PI intensity (au)",
      y = "log10 GFP intensity (au)",
    ) +
      guides(
    fill = guide_colorbar(
      barwidth  = unit(0.15, "in"),  # thinner bar
      barheight = unit(1.8, "in"),   # shorter height
      title.position = "top"
    )
  ) +
    theme_pubr() +
        scale_x_continuous(
      limits = c(-0.5, 3.75),
      breaks = c(0, 1, 2, 3)
    ) +
    scale_y_continuous(
      limits = c(-0.5, 3.75),
      breaks = c(0, 1, 2, 3)
    ) +
    theme(
   ## --- Facet labels & strips ---
    strip.placement = "outside",
    strip.background = element_blank(),
    strip.text.y.left = element_text(angle = 0, size = 14, margin = margin(1, 2, 1, 2, "pt")),
    strip.text.x = element_text(size = 14, margin = margin(2, 2, 2, 2, "pt")),
    ## --- Panel & grid ---
    aspect.ratio = 1,
    panel.grid = element_line(size = 0.2),
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 2),
    panel.spacing.x = unit(0.06, "in"),
    panel.spacing.y = unit(0.08, "in"),

    ## --- Axes ---
   ## Axis text
    axis.text = element_text(size = 14),  # match facet label size
    axis.title = element_text(size = 14, margin = margin(2, 2, 2, 2, "pt")),

    
    axis.ticks = element_blank(),        # remove ticks entirely
    axis.line = element_blank(),         # use panel.border instead


    ## --- Legend ---
    legend.position = "right",
    legend.margin = margin(0, 0, 0, 0, "pt"),
    legend.box.margin = margin(0, 0, 0, 0, "pt"),
    legend.key.height = unit(0.15, "in"),
    legend.key.width  = unit(0.15, "in"),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 14),

    ## --- Caption ---

    ## --- Outer margins ---
    plot.margin = margin(4, 6, 4, 6, "mm")
      ) +
    facet_grid(Abx.con ~ timestep, switch = "y") 


 # Keep square panels and make each facet ~2.5" wide/high
n_cols <- 7
n_rows <- 4
facet_width  <- 2.5  # inches per facet (tweak if you want bigger/smaller)
facet_height <- 2.5

# Optional: a touch more breathing room between panels
p <- p + theme(panel.spacing = grid::unit(0.15, "in"))

ggsave(
  filename = file.path(
    info.wd, "Experimental-Results",
    paste0(info.expID, "_FACS_gating_", strategy, "_20250815_Fig1_Manuscript.pdf")
  ),
  plot = p,
  width = n_cols * facet_width,   # 7 * 2.5 = 17.5 in
  height = n_rows * facet_height, # 3 * 2.5 = 7.5 in
  units = "in",
  device = "pdf"
)
}

```


```{r}
ASCTrep.df <- ASCTrep.df 
```




```{r}
library(dplyr)
library(ggplot2)
library(forcats)   # for fct_relevel

# -- ensure facet order & empty panels -----------------------------



# put Control last in the row order
abx_levels <- c("Control", setdiff(unique(ASCTrep.df$Abx.con), "Control"))

# apply factors to BOTH plotting df and labels df so facets align
ASCTrep.df <- ASCTrep.df %>%
  mutate(
    Abx.con = factor(Abx.con, levels = abx_levels),
    #timestep = factor(timestep, levels = ts_levels, ordered = TRUE)
        timestep = factor(timestep, levels = unique(timestep), ordered = TRUE)

  )

df_counts <- df_counts %>%
  mutate(
    Abx.con = factor(Abx.con, levels = abx_levels),
        timestep = factor(timestep, levels = unique(timestep), ordered = TRUE)

  #  timestep = factor(timestep, levels = ts_levels, ordered = TRUE)
  )

# -----------------------------------------------------------------

# Define parameters for each strategy
strategies <- c("gmm")
vlines <- c(threshold_PI_log_gmm)
hlines <- c(threshold_GFP_log_gmm)
linetypes <- c("dashed")
captions <- c(
  "Thresholds shown: Dashed lines = Gaussian Mixture Model thresholds GFP intensity for GFP threshold\n PI intensity for PI thrs using ATc control at t0"
)

thresholds_list <- list(
  gmm = list(
    GFP = threshold_GFP_log_gmm,
    PI  = threshold_PI_log_gmm
  )
)

# Loop through each strategy
for (i in seq_along(strategies)) {

  strategy <- strategies[i]
  str.filter <- strategy
  lt <- linetypes[i]
  caption_text <- captions[i]
  thrs <- thresholds_list[[strategy]]

  df_labels <- df_counts %>%
    filter(strategy == str.filter) %>%
    ungroup() %>%
    group_by(strategy, Abx.con, timestep) %>%
    mutate(
      label_text = paste0(
        round(percent, 1), "%\n",
        count, "\n"
      )
    )

  p <- ggplot(
    ASCTrep.df,
    aes(x = Mean.Intensity.POC.log10, y = Mean.Intensity.GOC.log10)
  ) +
    geom_hex(bins = 100) +
    scale_fill_gradientn(
      colors = zissou_cols,
      trans = "log10",
      name = "Cell count"
    ) +
    geom_vline(xintercept = thrs$PI,  linetype = lt, color = "black", linewidth = 0.8) +
    geom_hline(yintercept = thrs$GFP, linetype = lt, color = "black", linewidth = 0.8) +
    geom_text(
      data = df_labels,
      aes(x = x, y = y, label = label_text, group = interaction(Abx.con, timestep)),
      inherit.aes = FALSE,
      size = 4,
      lineheight = 0.9,
      color = "black"
    ) +
    labs(
      x = "log10 PI intensity (au)",
      y = "log10 GFP intensity (au)"
    ) +
    guides(
      fill = guide_colorbar(
        barwidth  = unit(0.15, "in"),
        barheight = unit(1.8, "in"),
        title.position = "top"
      )
    ) +
    theme_pubr() +
    scale_x_continuous(limits = c(-0.5, 3.75), breaks = c(0, 1, 2, 3)) +
    scale_y_continuous(limits = c(-0.5, 3.75), breaks = c(0, 1, 2, 3)) +
    theme(
      strip.placement = "outside",
      strip.background = element_blank(),
      strip.text.y.left = element_text(angle = 0, size = 14, margin = margin(1, 2, 1, 2, "pt")),
      strip.text.x = element_text(size = 14, margin = margin(2, 2, 2, 2, "pt")),
      aspect.ratio = 1,
      panel.grid = element_line(size = 0.2),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 2),
      panel.spacing.x = unit(0.06, "in"),
      panel.spacing.y = unit(0.08, "in"),
      axis.text = element_text(size = 14),
      axis.title = element_text(size = 14, margin = margin(2, 2, 2, 2, "pt")),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      legend.position = "right",
      legend.margin = margin(0, 0, 0, 0, "pt"),
      legend.box.margin = margin(0, 0, 0, 0, "pt"),
      legend.key.height = unit(0.15, "in"),
      legend.key.width  = unit(0.15, "in"),
      legend.title = element_text(size = 14),
      legend.text  = element_text(size = 14),
      plot.margin = margin(4, 6, 4, 6, "mm")
    ) +
    # IMPORTANT: keep empty panels for missing (e.g., Control at 2,4,6,8,20)
    facet_grid(Abx.con ~ timestep, switch = "y", drop = FALSE) +
    theme(panel.spacing = grid::unit(0.15, "in"))

  # Compute rows/cols from factor levels (Control is last by construction)
  
  n_cols <- length(levels(ASCTrep.df$timestep))
  n_rows <- length(levels(ASCTrep.df$Abx.con))
  facet_width  <- 2.5
  facet_height <- 2.5

  ggsave(
    filename = file.path(
      info.wd, "Experimental-Results",
      paste0(info.expID, "_FACS_gating_", strategy, "_20250815_Fig1_Manuscript.pdf")
    ),
    plot = p,
    width  = n_cols * facet_width,
    height = n_rows * facet_height,
    units = "in",
    device = "pdf"
  )
}

```


```{r}
rm(thrs,
   thresholds_list,
   pos_map,
   PI_control,
   p,
   FACS,
   df_long_all,
 
   GFP_control,
   ASCTrep.filtered)
```

