
# ================================================================
# Aim
# ================================================================
# This script aggregates Trkv2 time-kill data across ASCT experiments
# to generate mean 7-day time-kill curves for MTB isolates, grouped
# by drug and experiment.

# Functions:
# - Load Trkv2 tracking (LCF_flags) and raw KF outputs for all
#   experiments in ASCT_Data.
# - Apply QC filters (Overall.Assessment == "Keep", Multiple.Events == "Keep")
#   and keep only wells with valid KF endpoints.
# - Align KF endpoint to the tracking timeline and adjust Time_Hrs
#   using loopAB / loopBC offsets for long experiments.
# - Compute mean live-cell fraction over time per drug × isolate.
# - Annotate experiments with the number of drugs tested.
# - Plot mean time-kill curves (percent cells alive) for each isolate,
#   coloured by drug, faceted by experiment, and export as a PDF.

# Section 1: Defining variables
```{r setup, include=FALSE}

genDir <- getwd() 


#Pop data variables
data.dir <- c("ASCT_Data")
res.dir <- c("Experimental-Results")

type.of.analysis <- c("Wellbased.Fitting")

exp.res.dir <- c(paste(genDir,
                       "/",
                       "Experimental-Results",sep=""))
wdDir <- genDir

res.dir <- paste(genDir,"/",res.dir ,sep="")

data.dir <- paste(genDir,
                  "/",
                  data.dir,
                  sep="")
setwd(wdDir)

# list the experiment directories to pull the tracking data

loopAB <- 2
loopBC <- 4


# EDIT the time scale axis that should be used 
plot.xaxis.time.scale <- c(0, 12, 24, 36, 48, 60, 72, 84, 96, 108, 120, 132, 144, 156, 168, 180)

```

# Section 2: Loading packages
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels) 
library(MESS)
library(gghighlight)
library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)

```

## 2.1 Loop through Experimental Results
```{r}

Main.Tracking.df <- data.frame()

Main.KF.df <- data.frame()

# Load KF.intermediary table
KFinter.files <- list.files(data.dir, pattern = "_Trkv2_KFintermediary.csv", full.names = TRUE)
i <- KFinter.files[1]
for ( i in     KFinter.files ) {
    
  
  KF.intermediary.df <- read.csv(i)
    print(i)
         KF.intermediary.df <-   KF.intermediary.df %>%
           filter(Merge.def == "Trkv2_Ila2BaSic")%>%
           select(ExpFile,
                  Abx.con,
                  Well_coordinate,
                  Multiple.Events)%>%
           distinct()

         x <- sub(
                  "_Trkv2_KFintermediary.csv$",
                  "_Trkv2_LCF_flags.csv",i)
    
  # Load Trkv2 Flags

  Tracking.df <- read.csv(   x )
  
    Tracking.df <-   Tracking.df %>%
      filter(Time.Kill.Definitions == "Trkv2_LCF_Ila2BaSic")%>%
      left_join(         KF.intermediary.df )
    
    
    Main.Tracking.df <- rbind(    Main.Tracking.df,
                                     Tracking.df )
    
    

 x <- sub(
              
                  "_Trkv2_LCF_flags.csv$",
                   "_Trkv2_rawKF.csv",
                  i)
        
    KFraw <- read.csv(   x )
    
    KFraw <-KFraw %>%
      filter(Killing.Def == "Trkv2_LCF_Ila2BaSic")
    
    
    Main.KF.df <- rbind(    Main.KF.df ,   KFraw )
    

    }
    


  rm(KF.intermediary.df,
     KFraw,
     Tracking.df)

```



```{r}
# ---

Main.KF.df <- Main.KF.df %>%
  mutate(Killing.Def = gsub("Trkv2_LCF_Ila2BaSic","Trkv2_Ila2BaSic", Killing.Def))
  

Main.KF.df <- Main.KF.df %>%
  mutate(Sub.KF = Killing.Features)%>%
  mutate(Sub.KF = gsub("Trkv2_LCF_","",Sub.KF))%>%
    mutate(Sub.KF= gsub("_Ila2BaSic", "",Sub.KF))%>%
  mutate(Time_Hrs = gsub("h","",Sub.KF)) %>%
  mutate(Time_Hrs = as.numeric(Time_Hrs))%>%
  mutate(Time.Kill.Definitions = Killing.Def)%>%
  mutate(LC.fraction.corr = value)%>%
  mutate(ExpFile.Wellcoordinate = paste(ExpFile,
                                        Well_coordinate,
                                        sep="_"))%>%
  select(ExpFile,
         Abx.con,
         Isolate,
         ExpFile.Wellcoordinate ,
         Well_coordinate,
         Time_Hrs,
         Time.Kill.Definitions ,
         LC.fraction.corr)%>%
  distinct()%>%
  filter(Time_Hrs == max(plot.xaxis.time.scale)) 
  


# ---
Main.Tracking.df <- Main.Tracking.df %>%
  ungroup()%>%
  filter(Overall.Assessment == "Keep" &
           Multiple.Events == "Keep")


Main.Tracking.df <- Main.Tracking.df %>%
  mutate(ExpFile.Wellcoordinate = paste(ExpFile,
                                        Well_coordinate,
                                        sep="_"))
 

Main.Tracking.df <- Main.Tracking.df %>%
mutate(timestep = as.numeric(timestep))


list.of.Well.coordinates.Kept.in.analysis <- unique(Main.Tracking.df$ExpFile.Wellcoordinate)

Main.KF.df <- Main.KF.df %>%
  filter(ExpFile.Wellcoordinate %in% list.of.Well.coordinates.Kept.in.analysis)

Main.KF.df <- Main.KF.df %>%
  mutate(timestep = as.numeric(max(Main.Tracking.df$timestep)+1))

# Assume your y-axis linear scale values range from 1 to 100%

linear_breaks <- c( 40,50,60 ,70,80,90, 100) # Modify this based on your data

# Convert these to log10 scale for the breaks
log_breaks <- log10(linear_breaks)

Main.Tracking.df <- Main.Tracking.df %>%
  mutate(ExpID =paste("ASCT.",
                      gsub("^.*\\.(.*)\\..*$", "\\1", ExpFile),
                      sep=""))

Main.KF.df  <- Main.KF.df %>%
  mutate(ExpID =paste("ASCT.",
                      gsub("^.*\\.(.*)\\..*$", "\\1", ExpFile),
                      sep=""))


```

# Merging Killing Features and Main tracking Data 
```{r}

Exp.QC <- Main.Tracking.df %>%
  select(ExpFile,
         Well_coordinate,
         Flag.label,
         Overall.Assessment,
         Multiple.Events)%>%
  distinct()
  

variable_names <- names(Main.KF.df)

Main.Tracking.df <- Main.Tracking.df %>%
   select(all_of(variable_names))

Main.KF.df  <- Main.KF.df %>%
  mutate(Time.Kill.Definitions = if_else(Time.Kill.Definitions == "Trkv2_Ila2BaSic", "Trkv2_LCF_Ilas2BaSic", Time.Kill.Definitions))
  
Main.Tracking.df <- rbind(Main.Tracking.df,
                          Main.KF.df)

Main.Tracking.df <- Main.Tracking.df %>%
  left_join(Exp.QC)


rm(Exp.QC)


```


```{r}


# Modify the dataframe
Main.Tracking.df <- Main.Tracking.df %>%
  group_by(ExpID, Isolate, Abx.con,Well_coordinate) %>% # Group by the specified columns
  mutate(
    Time_Hrs = ifelse(timestep >= 19 , Time_Hrs + loopAB,
                      ifelse(timestep >= 37, Time_Hrs +  loopAB + loopBC, Time_Hrs)) # Add hours based on timestep
  )

```

```{r}
library(stringr)
Main.Mean.Tracking.df<- Main.Tracking.df %>%

  group_by(#ExpFile,
           Abx.con,
           Isolate,
           timestep)%>%
mutate(Mean.LC.fraction.corr = mean(LC.fraction.corr),
         Mean.Time_Hrs = mean(Time_Hrs))%>%
  ungroup()%>%
  filter(Time_Hrs <= max(plot.xaxis.time.scale))%>%
  select(ExpID,
         Time.Kill.Definitions,
         Abx.con,
         Isolate,   
         Mean.Time_Hrs,
         Mean.LC.fraction.corr)%>%
  distinct()%>%
  mutate(Drug=   sub("_.*", "", Abx.con)  )%>%
  mutate(Isolate = gsub("7h9","pan",Isolate))%>%
  mutate(Isolate = gsub("log","",Isolate))%>%
  mutate(Type.of.Analysis = type.of.analysis)%>%
  filter(!Drug %in% c("Ka", "Kb", "Kc", "NodDrug"))%>%
  filter(Isolate != "Iso.Hipos")
```


```{r}
#----------

N.drugs.In.exp <- Main.Mean.Tracking.df %>%
  select(Drug)%>%
  distinct()
 
N.drugs.In.exp<-   nrow(N.drugs.In.exp)



Conditions.df.Drugs.perExp <- Main.Mean.Tracking.df %>%
  select(ExpID,
         Drug,
         Isolate)%>%
  distinct()%>%
  group_by(ExpID,
           Isolate)%>%
  mutate(N.Drugs.per.Exp =1,
         N.Drugs.per.Exp = sum(N.Drugs.per.Exp ))%>%
  ungroup()%>%
  mutate(        N.Drugs.per.Exp = paste(N.Drugs.per.Exp,
                                  "/",
                                N.drugs.In.exp ,
                                  sep=""))%>%
  ungroup()%>%
  select(ExpID,
          Isolate,
          N.Drugs.per.Exp)%>%
  distinct()


Main.Mean.Tracking.df <- left_join(Main.Mean.Tracking.df ,
                           Conditions.df.Drugs.perExp)


Main.Mean.Tracking.df <- Main.Mean.Tracking.df %>%
 mutate(N.Drugs.per.Exp = paste("N.drugs: ",
                                 N.Drugs.per.Exp,
                                 sep=""))



rm(N.drugs.In.exp,
   Conditions.df.Drugs.perExp)


x <- unique(Main.Mean.Tracking.df$Abx.con)
```




```{r}
plot.filename <- paste(exp.res.dir, "/ASCTmtb_Mean_TimeKillcurve_7dayExp_", type.of.analysis,"_loopAB",loopAB,"h_loopBC", loopBC, "h_MTBmc27000.pbs.Starved_StandardTreatment.pdf", sep = "")

x_values <- c(3, 6, 9, 12, 24, 48)

#--- Y axis ticks

linear_breaks <- c(0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.0) # Modify this based on your data

# Convert these to log10 scale for the breaks
log_breaks <- log10(linear_breaks)

linear_breaks.label <- c(40, 50, 60, 70, 80, 90, 100)
#---

# Set colors based on the drug names
Main.Mean.Tracking.df <- Main.Mean.Tracking.df %>%
  mutate(color = case_when(
    Drug == "EHRZ" ~ "darkblue",
    Drug == "HR" ~ "steelblue",
    Drug == "BLPa" ~ "red",
    Drug == "BPaZ" ~ "purple",

    grepl("B|Pa|C", Drug) ~ "darkgreen",
    TRUE ~ "black"
  ))

library(ggrepel)
gg <- Main.Mean.Tracking.df %>%
  mutate(Mean.LC.fraction.corr = Mean.LC.fraction.corr * 100) %>%
  filter(Mean.Time_Hrs <= max(plot.xaxis.time.scale)) %>%
  filter(Isolate == "Iso.mc27000pbsStrvd") %>%
  ungroup() %>%
  ggplot(aes(x = Mean.Time_Hrs,
             y = Mean.LC.fraction.corr,
             group = Drug,
             label = Drug,
             colour = color)) +  # Use the color column for colors
  geom_line(alpha = 0.50, size = 0.2, stroke = 0) +
  scale_colour_identity() +  # Use the colors as defined
  theme_prism(base_line_size = 0.2) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100),
                     limits = c(0, 100),
                     labels = c(0, 20, 20, 60, 80, 100)) +
  theme(axis.text = element_text(size = 7)) +
  theme(strip.text.x = element_text(size = 7)) +
  theme(legend.key.size = unit(0.1, "cm"),
        legend.key.width = unit(0.1, "cm")) +
  scale_x_continuous(breaks = plot.xaxis.time.scale) +
  labs(title = paste("Mean time kill kinetics of MTb Isolates loopAB", loopAB, "h loopBC", loopBC ,"h", sep=""),
       subtitle = "linear scale",
       x = "Time [Hrs]",
       y = "Percent of cells alive [%]",
       color = "Drugs") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1) +
  theme(plot.subtitle = element_text(size = 7)) +
  theme(legend.position = "none") +  # Removes the legend
  facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 1,
                      nrow = 1,
                      page = 1)

n <- n_pages(gg)

pdf(plot.filename, paper = "a4", width = 20, height = 15)
for(i in 1:n){
    print(gg + facet_wrap_paginate(ExpID + N.Drugs.per.Exp + Type.of.Analysis ~ Isolate,
                      ncol = 1,
                      nrow = 1, page = i)) ## WORKS with 240 wells ## I think Error: Cannot create zero-length unit vector ("unit" subsetting) means it does not know how to plot the remaining 2 wells on the last page given ncol 4 and nrow 6
}
dev.off()

# Housekeeping
rm(gg, plot.filename, g)


```
