---
title: "ASCT kill curves histogram"
output: html_document
date: "2024-04-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Definig paths
```{r}
wdDir <- getwd()

setwd(wdDir)
resDir <- paste(wdDir,
                "/",
                "Result_Fig",
                sep="")

dataDir <- paste(wdDir,
                "/",
                "ASCT_Data",
                sep="")

mic.sub.range <- paste(wdDir,
                "/",
                "Info/Ranges_of_MIC_to_use_subset.xlsx",
                sep="")

```

# Load libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggExtra)
library(readxl)
library(reshape2)

library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels) 
library(MESS)
library(gghighlight)
library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)



```

# Loading Data
```{r}
#MIC
MIC.df <- read.csv("/Users/jovanovic/Documents/PhD/Project_Tolerance/Ranalysis/ASCT/ASCT_Figures/ASCT_Main_Data/MainPhenotypes_ASCTpaper.csv")

MIC.df <-MIC.df %>%
   select(matches("_MIC_|Isolate|ClearedVSpersistant_ATS"))

MIC.df <- melt(MIC.df ,
               id.vars = c("Isolate",
                           "ClearedVSpersistant_ATS"),
                variable.name = "Abx.con",
               value.name = "MIC")

MIC.df <- MIC.df %>%
  mutate(ClearedVSpersistant_ATS = if_else(is.na(ClearedVSpersistant_ATS), 3, ClearedVSpersistant_ATS))#Category 3 means Unkown outcome



Outcome.df <- MIC.df %>%

  select(Isolate,
         ClearedVSpersistant_ATS)%>%
  drop_na()%>%
  distinct()

MIC.df <-MIC.df %>%
  select(Isolate,
         Abx.con,
         MIC)%>%
  drop_na()



MIC.Single.barplot.df <- MIC.df
```


```{r}
MIC.outcome.df <-left_join(Outcome.df,
                           MIC.df)

MIC.outcome.df <-MIC.outcome.df %>%
mutate(ClearedVSpersistant_ATS = if_else(ClearedVSpersistant_ATS == 1, "Persistant",
                                    if_else(ClearedVSpersistant_ATS == 0, "Cleared" ,"Unkown")))


MIC.outcome.df <-MIC.outcome.df %>%
drop_na()

MIC.outcome.df <-MIC.outcome.df %>%
  mutate(N.per.Outcome = 1)%>%
  group_by(Abx.con,
           MIC,
           ClearedVSpersistant_ATS
           )%>%
  mutate(N.per.Outcome =sum(N.per.Outcome))

```


# Combined dual axis plot



## Fix plot based on discussion with LB

LB % of outcome should reflect the trend of the bars similar like a histogram. Adjust calculation to be per abx per outcome.
# Percent MIC plot per Abx per Outcome category
```{r}
# Assuming MIC.outcome.df is your data frame as described.
# First, you need to group by both 'Abx.con' and 'ClearedVSpersistant_ATS' to calculate the sums of 'N.per.Outcome' for each category.

MIC.perc.outcome.Updated.df <- MIC.outcome.df %>%
  ungroup()%>%
  select(Abx.con,
         ClearedVSpersistant_ATS,
         Abx.con,
         MIC,
         N.per.Outcome)%>%
  distinct()%>%
  group_by(Abx.con,
           ClearedVSpersistant_ATS) %>%
  mutate(Total_perAbx.perOutcome = sum(N.per.Outcome) )%>%
  ungroup()%>%
  group_by(Abx.con,
           ClearedVSpersistant_ATS,
           MIC)%>%
  mutate(Percent_perMIC = round((N.per.Outcome / Total_perAbx.perOutcome)*100, digits = 1))%>%
  ungroup()%>%
  select(Abx.con,
           ClearedVSpersistant_ATS,
           MIC,
         Percent_perMIC)%>%
  distinct()

# Calculate the maximum to scale secondary axis appropriately
div.factor.scale <- max(MIC.outcome.df$N.per.Outcome , na.rm = TRUE)

# Adjust the percent values to align with the primary y-axis scale
max.percent <- max(MIC.perc.outcome.Updated.df$Percent_perMIC)
scaling.factor <- div.factor.scale / max.percent  # Calculate the scaling factor for the secondary axis

 

```


# Make between Anitbiotic concentrations if there is gap e.g. 1,2,3,6,7,8 make 4 ,5 zero values
```{r}
library(dplyr)
library(tidyr)

# Assuming MIC.outcome.df is your dataframe

# Generate all combinations of Abx.con, MIC, and ClearedVSpersistant_ATS with complete MIC range
expanded_df <- MIC.outcome.df %>%
  group_by(Abx.con, ClearedVSpersistant_ATS) %>%  # THIS WORKS 
  #  group_by(Abx.con) %>%
  summarize(MIC_range = list(seq(min(MIC), max(MIC))), .groups = "drop") %>%
  unnest(c(MIC_range)) %>%
  rename(MIC = MIC_range)

# Join expanded_df with original to get all original data back
# Filling missing N.per.Outcome values with 0
full_df <- expanded_df %>%
  left_join(MIC.outcome.df, by = c("Abx.con", "ClearedVSpersistant_ATS", "MIC")) %>% # KEEP
  mutate(N.per.Outcome = ifelse(is.na(N.per.Outcome), 0, N.per.Outcome))


full_df <- full_df %>%
ungroup()%>%
  select(Abx.con,
         ClearedVSpersistant_ATS,
         Abx.con,
         MIC,
         N.per.Outcome)%>%
  distinct()%>%
  group_by(Abx.con,
           ClearedVSpersistant_ATS) %>%
  mutate(Total_perAbx.perOutcome = sum(N.per.Outcome) )%>%
  ungroup()%>%
  group_by(Abx.con,
           ClearedVSpersistant_ATS,
           MIC)%>%
  mutate(Percent_perMIC = round((N.per.Outcome / Total_perAbx.perOutcome)*100, digits = 1))%>%
  ungroup()%>%
  select(Abx.con,
           ClearedVSpersistant_ATS,
           MIC,
         Percent_perMIC,
         N.per.Outcome)%>%
  distinct()


# Calculate the maximum to scale secondary axis appropriately
div.factor.scale <- max(full_df$N.per.Outcome , na.rm = TRUE)



max.percent <- 100
scaling.factor <- div.factor.scale / max.percent  # Calculate the scaling factor for the secondary axis
```



```{r}

 rm(full_df,
    expanded_df)

```

# Single bar plot representing all MIC counts with lines represening outcome
```{r}
MIC.Single.barplot.df <- MIC.df %>%
  mutate(N.per.MIC = 1)%>%
  group_by(Abx.con,
           MIC) %>%
  mutate(N.per.MIC = sum(N.per.MIC))%>%
  ungroup()%>%
  select(Abx.con,
         MIC,
         N.per.MIC)%>%
  distinct()
  
  
  # Assuming MIC.outcome.df is your dataframe

# Generate all combinations of Abx.con, MIC, and ClearedVSpersistant_ATS with complete MIC range
 MIC.Single.barplot.df.expanded <- MIC.Single.barplot.df %>%
   group_by(Abx.con) %>%
  summarize(MIC_range = list(seq(min(MIC), max(MIC))), .groups = "drop") %>%
  unnest(c(MIC_range)) %>%
  rename(MIC = MIC_range)

# Join expanded_df with original to get all original data back
# Filling missing N.per.Outcome values with 0
 MIC.Single.barplot.df.full <- MIC.Single.barplot.df.expanded %>%
  left_join(MIC.Single.barplot.df, by = c("Abx.con",  "MIC")) %>% # KEEP
  mutate(N.per.MIC = ifelse(is.na(N.per.MIC), 0, N.per.MIC))
 
 
 # Make sure to fill the gaps with the range of MIC of the outcome plots
 
 # Generate all combinations of Abx.con, MIC, and ClearedVSpersistant_ATS with complete MIC range
MIC.perc.outcome.Update.expanded <- MIC.perc.outcome.Updated.df %>%
   group_by(Abx.con) %>%
  summarize(MIC_range = list(seq(min(MIC), max(MIC))), .groups = "drop") %>%
  unnest(c(MIC_range)) %>%
  rename(MIC = MIC_range)%>%
   mutate(Outcome1 ="Unkown",
          Outcome2 = "Persistant",
          Outcome3 ="Cleared")

# Create the new data frame



MIC.perc.outcome.Update.expanded <- melt(MIC.perc.outcome.Update.expanded ,
               id.vars = c("Abx.con",
                           "MIC"),
                variable.name = "ClearedVSpersistant_ATS")%>%
  select(-ClearedVSpersistant_ATS)%>%
  mutate(ClearedVSpersistant_ATS = value)%>%
  select(-value)%>%
  mutate(MIC = as.numeric(MIC))

#"ClearedVSpersistant_ATS"
```


```{r}
MIC.perc.outcome.Update.full <- MIC.perc.outcome.Update.expanded %>%
  left_join(MIC.perc.outcome.Updated.df, by = c("Abx.con",
                                          "MIC",
                                          "ClearedVSpersistant_ATS")) %>% # KEEP
  ungroup()%>%
  filter(ClearedVSpersistant_ATS != "Unkown")%>%
  #group_by(ClearedVSpersistant_ATS)%>%
  mutate(Percent_perMIC = ifelse(is.na(Percent_perMIC),
                                 0,
                                 Percent_perMIC))

 rm(full_df,
    expanded_df,
   MIC.perc.outcome.Update.expanded,
   MIC.Single.barplot.df.expanded)

scaling.factor <- max(MIC.Single.barplot.df.full$N.per.MIC) / max.percent  # Calculate the scaling factor for the secondary axis

div.factor.scale <-  max(MIC.Single.barplot.df.full$N.per.MIC)

```


# Plot with µg/ml 

```{r}

abx_data <- read_xlsx(mic.sub.range ) 

abx_data <- abx_data %>%
  mutate(MIN = `MIN [ug/ml]`,
         MAX = `MAX [ug/ml]`,
         log2_steps = `log2-steps`)%>%
  select(Abx.con,
         MIN,
         MAX,
         log2_steps)

# Expand the dataframe into long format
MICµg.gg <- abx_data %>%
  rowwise() %>%
  do({
    data.frame(Abx.con = .$Abx.con,
               MIC = exp(log(.$MIN) + seq(0, log(.$MAX/.$MIN), length.out = .$log2_steps)),
               Step = seq_len(.$log2_steps))
  })


# View the resulting dataframe

rm(abx_data)




MICµg.gg_MIC.Single.barplot.df<- MIC.Single.barplot.df.full%>%
  mutate(MIC = 2^ MIC)%>%
  mutate(MIC_original = MIC)%>%
    mutate(MIC = formatC(MIC, format = "f", digits = 4))%>%
      mutate(MIC = if_else(MIC =="0.0313", "0.0312" , MIC))%>%
 #  mutate(MIC = round(MIC))%>%
    mutate(Abx.con = gsub("_MIC_lg2", "", Abx.con))



MICµg.gg  <- MICµg.gg %>%
  mutate(MIC_plot_label = MIC)%>%
 # mutate(MIC = round(MIC))
  mutate(MIC = formatC(MIC, format = "f", digits = 4))%>%
  mutate(MIC = if_else(MIC =="0.0313", "0.0312" , MIC))



MICµg.gg_MIC.perc.outcome.Update.full <- MIC.perc.outcome.Update.full %>%
   mutate(MIC = 2^ MIC)%>%
  mutate(MIC_original = MIC)%>%
    mutate(MIC = formatC(MIC, format = "f", digits = 4))%>%
    mutate(MIC = if_else(MIC =="0.0313", "0.0312" , MIC))%>%
 #  mutate(MIC = round(MIC))%>%
    mutate(Abx.con = gsub("_MIC_lg2", "", Abx.con))
  
MICµg.gg_MIC.perc.outcome.Update.full_TEST <- MICµg.gg%>%
  left_join(MICµg.gg_MIC.perc.outcome.Update.full )%>%
  drop_na()%>%
    mutate(across(everything(), ~replace_na(., 0)))


# Perform the left join
NEW <- left_join(MICµg.gg,  
                 MICµg.gg_MIC.Single.barplot.df)

NEW <- NEW %>%
    mutate(across(everything(), ~replace_na(., 0)))



order.of.MICs <- sort(as.numeric(unique(NEW$MIC)))

order.of.MICs <- as.character(order.of.MICs )



order.of.MICs <- c("0.0002", "0.0005", "0.0010", "0.0020", "0.0039", "0.0078", "0.0156", "0.03125", "0.0312","0.0313",  "0.0625", 
                   "0.125", "0.25", "0.5", "1", "2", "4", "8", "16", "32", "64", 
                   "128", "256", "512", "1024")


order.of.MICs

BDQ <- NEW %>%
  filter(Abx.con == "BDQ")


trim_zeros <- function(x) {
  # Remove trailing zeros and a decimal point if it ends with one
  x <- sub("\\.?0+$", "", x)
  return(x)
}


NEW$MIC <- sapply(NEW$MIC, trim_zeros)


MICµg.gg_MIC.perc.outcome.Update.full_TEST$MIC  <-sapply(MICµg.gg_MIC.perc.outcome.Update.full_TEST$MIC, trim_zeros)
```


# Reduced  MIC dynamic range 

```{r}
plot.path <- paste(resDir,
                     "/",
  "ASCTfig_MIC_Alldata_MICbarplot_Outcome_curves_MICµgml_subMICrange-FreeScale-ExclRFB.BDQ.pdf",
  sep="")
 
 NEW.exl <- NEW %>%
  filter(Abx.con != "RFB", Abx.con != "BDQ")
 
 
 MICµg.gg_MIC.perc.outcome.Update.full_TEST.exl <- MICµg.gg_MIC.perc.outcome.Update.full_TEST %>%
     filter(Abx.con != "RFB", Abx.con != "BDQ")

pdf(plot.path)

NEW.exl %>%
  filter(Abx.con != "RFB", Abx.con != "BDQ") %>%
  mutate(MIC = factor(MIC, levels = order.of.MICs)) %>%
  distinct() %>%
  drop_na() %>%
  ggplot(aes(x = MIC)) +
  geom_bar(aes(y = N.per.MIC),
           stat = "identity",
           position = "dodge2",
           alpha = 0.75) +
  geom_line(data = MICµg.gg_MIC.perc.outcome.Update.full_TEST.exl,
            aes(y = Percent_perMIC * scaling.factor,
                color = ClearedVSpersistant_ATS,
                group = ClearedVSpersistant_ATS), 
            alpha = 0.5, 
            size = 0.2) +
  geom_point(data = MICµg.gg_MIC.perc.outcome.Update.full_TEST.exl,
             aes(y = Percent_perMIC * scaling.factor,
                 color = ClearedVSpersistant_ATS,
                 group = ClearedVSpersistant_ATS),
             alpha = 0.8, 
             stroke = 0,
             size = 0.5) +
 
  
  scale_y_continuous(
  name = "Number of isolates per MIC",
  limits = c(0, div.factor.scale), 
  sec.axis = sec_axis(~ . / scaling.factor,
                      name = "Percent per clinical outcome(%)",
                      breaks = seq(0, 100, by = 20),
                      labels = scales::label_number(accuracy = 1)
                      ) 
) +
  scale_fill_manual(values = c("Cleared" = "navyblue",
                               "Persistant" = "red")) +
  scale_color_manual(values = c("Cleared" = "navyblue", 
                                "Persistant" = "red")) + # Matching color for the lines
  labs(title = "Distribution of MIC by Antibiotic and Outcome", 
       x = "MIC µg/ml",
       fill = "ClearedVSpersistant_ATS") +
  theme_prism(base_line_size = 0.2) +
  theme(text = element_text(size = 7))+
  theme(axis.line.y.right = element_line(color = "black"), 
        axis.ticks.y.right = element_line(color = "black"),
        axis.text.y.right = element_text(color = "black", size = 3), 
        axis.text.y = element_text(color = "black", size = 7), 
  axis.text.x = element_text(color = "black", size = 7, angle = 45, vjust = 1, margin = margin(t = 2)), 
        axis.ticks.length = unit(0.025, "cm"),
        legend.position = "top",           # Position the legend at the top
        axis.title = element_text(size = 16, face = "plain"),  # Axis titles not bold
        axis.text = element_text(size = 14, face = "plain"),   # Axis text not bold
        legend.title = element_text(size = 14, face = "plain"),# Legend title not bold
        legend.text = element_text(size = 12, face = "plain"), # Legend text not bold
        plot.title = element_text(size = 18, face = "plain"),  # Plot title not bold
        axis.title.y.right = element_text(color = "black")) +
  facet_wrap(~Abx.con, scales = "free")

dev.off()


```

