---
title: "ASCT_check_MAB_associations"
output: html_document
date: "2024-10-15"
---

# 1. Set directories
```{r}

info.wd <- getwd()

info.resDir <- paste(info.wd,
                     "/Fig_results/",
                     sep="")


info.dataDir <- c("/Users/jovanovic/Documents/PhD/Project_Tolerance/Ranalysis/ASCTmtb/ASCTmtb_EXPERIMENTS/ASCTmtb_OverviewAssociations_perWell/Experimental-Results/ALLdata_MTB_resultstable_perWell.fitting_20241017_LB.csv") 



```
# 2. Load libraries
```{r}

library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels)
library(MESS)
library(gghighlight)
library(scales)
library(GGally)
library(ggcorrplot)
library(reshape2)
library(plotrix)
library(ggprism)
library(ggrepel)
library(stringr)
library(readxl)
library(rstatix)
library(ggExtra)


library(grid)  # Load the grid package allows you to add text to pages in ggplot
library(coin)
```

# 3. Load main data
```{r}
Main.df <- read.csv(info.dataDir)



MTB <- Main.df %>%
  select( RMM.2021,
          BMM.2021,
          BMM.BHeB.2021,
          Clinical.2022,
         matches("AUC.0.168h_"),
          matches("lg2."))

```


# 3.1 Select key variables and perform mann whitney U test
```{r}

list.of.variables <- names(MTB)

list.of.outcomes <- c("RMM.2021",
                      "BMM.2021",
                      "BMM.BHeB.2021",
                      "Clinical.2022")



list.of.variables <- setdiff(list.of.variables, list.of.outcomes)
list.of.variables <- c(
  "lg2.min.MIC.ug.ml..d14_Iso.H37Ra",
  "lg2.median.MIC.ug.ml..d14_Iso.H37Ra",
  "lg2.mean.MIC.ug.ml..d14_Iso.H37Ra",
  "lg2.min.MIC.ug.ml..d14_Iso.mc27000",
                       "lg2.median.MIC.ug.ml..d14_Iso.mc27000",
                       "lg2.mean.MIC.ug.ml..d14_Iso.mc27000" )


var <- list.of.variables[1]
outcome <- list.of.outcomes[1]
MTB.stats <- data.frame()


for ( outcome in list.of.outcomes ) {
  
  
  for ( var in list.of.variables ) {
  
    
    if ( outcome ==   "Clinical.2022") {
       # Statistical test RMM2021
  MTB.sub <- MTB %>%
    select(outcome,
           var)%>%
    drop_na()%>%
  filter_all(all_vars(. != "ND")) %>%
  filter_all(all_vars(. != "C2-")) %>%
 mutate(
    across(all_of(outcome), as.factor),  # Convert outcome column to factor
    across(all_of(var), as.numeric)      # Ensure var column is numeric
  )
  
  # Apply the Wilcoxon test with dynamically created formula
test_result <- coin::wilcox_test(as.formula(paste(var, "~", outcome)), data = MTB.sub, 
                                 distribution = "exact")

#extracting p values
p_value <- pvalue(test_result)
MTB.stats.sub <- data.frame(
  Metric = var,
  In.vivo.outcome =outcome ,
  Stat.test = "mwu.test",
  p = p_value)
  
   MTB.sub.export <- MTB %>%
    select(outcome,
           var)%>%
    drop_na()%>%
  filter_all(all_vars(. != "ND")) %>%
  filter_all(all_vars(. != "C2-"))
   
    write.csv(  MTB.sub.export,
              paste(info.resDir,
                    "/Intermediary_Files_AJ/",
                    "R.mwu_AJcoin_",
                    var,
                    "_",
                    outcome,
                    ".csv",sep=""),
              row.names = FALSE)
  
      
    } else {
         # Statistical test RMM2021
  MTB.sub <- MTB %>%
    select(outcome,
           var)%>%
      drop_na()%>%
    filter_all(all_vars(. != "ND")) %>%
    mutate(
    across(all_of(outcome), as.factor),  # Convert outcome column to factor
    across(all_of(var), as.numeric)      # Ensure var column is numeric
  )
  # Apply the Wilcoxon test

# Apply the Wilcoxon test with dynamically created formula
test_result <- coin::wilcox_test(as.formula(paste(var, "~", outcome)), data = MTB.sub, 
                                 distribution = "exact")
#extracting p values
p_value <- pvalue(test_result)

MTB.stats.sub <- data.frame(
  Metric = var,
  In.vivo.outcome =outcome ,
  Stat.test = "mwu.test",
  p = p_value)


  MTB.sub.export <- MTB %>%
    select(outcome,
           var)%>%
      drop_na()%>%
filter_all(all_vars(. != "ND")) 
  
  write.csv(  MTB.sub.export,
              paste(info.resDir,
                    "/Intermediary_Files_AJ/",
                    "R.mwu_AJcoin_",
                    var,
                    "_",
                    outcome,
                    ".csv",sep=""),
              row.names = FALSE)
      
    }

  
  
  MTB.stats <- rbind(MTB.stats,
                            MTB.stats.sub)
  
  
                 
}
}

# Get the current date and time in YYYYMMDD_HH format
current_date_time <- format(Sys.time(), "%Y%m%d_%H")

rm(MTB.sub)
```

# 5. Export result table
```{r}


write.csv(MTB.stats , 
          paste(info.resDir,"ASCT_MTBassociation_mwu.statistics_",current_date_time,"_AJmicdata_coin.csv",sep=""), row.names = FALSE)

MTB.stats.wide <- MTB.stats 



MTB.stats.wide <- MTB.stats.wide %>%
  pivot_wider(
    names_from = In.vivo.outcome,      # Use `.y.` to create new column names
    values_from = p        # Spread values from `p` across those new columns
  )


write.csv(MTB.stats.wide , 
          paste(info.resDir,"ASCT_MTBassociation_mwu.statistics_",current_date_time,"_WIDE_AJmicdata_coin.csv",sep=""), row.names = FALSE)

```

# Supplementary Figure 2
## Assciation with and without distinct drug combinaitons
### With Ethambutol, Isoniazid, Rifampicin, Bedaquiline,Pretomanid, Clofazimine
```{r}
list.of.distinct.drugs <- c(
  "E",#Ethambutol
     "H",#Isoniazid
     "R",#Rifampicin
     "B", #Bedaquiline
     "Pa",#Pretomanid
     "C", #Clofazimine
     "Su",#Sutezolid
     "P",#Refapentin
     "Z", # Pyrazinamid
     "M",#Moxifloxacin 
     "Sq",#SQ109
     "D",#Delamanid
     "L"#Linezolid
     )

list.of.all.drugs <- unique(Main.df$Drug)

MTB.select <- Main.df %>%
  select(Drug,
           matches("AUC.0.168h_"))


list.of.variables <- setdiff(names(MTB.select), "Drug")
list.of.AUC.variables <- names(MTB.select)[grepl("AUC.0.168", names(MTB.select))]

str(MTB.select)

# 
 auc.var <-list.of.AUC.variables[3]
distinct.drug <- list.of.distinct.drugs[6] # P

#----
MTB.select.stats <- data.frame()
MTB.select.growing.IntermedRes <- data.frame()
MTB.select.starved.IntermedRes <- data.frame()


# Iterate through list of distinct drugs
for ( distinct.drug in list.of.distinct.drugs) {
  if (distinct.drug == "P") {
  MTB.select.sub <- MTB.select %>%
    mutate(Split_drugs = gsub("([A-Z])", "_\\1", Drug) %>% gsub("^_", "", .)) %>%
    mutate(With_withoutDrug = ifelse(grepl(paste("_", distinct.drug, "_", sep = ""), Split_drugs),
                                     distinct.drug,
                                     paste("no ", distinct.drug, sep = ""))) %>%
    select(Drug, With_withoutDrug, everything())
  
} else if (distinct.drug == "Pa") {
  MTB.select.sub <- MTB.select %>%
    mutate(Split_drugs = gsub("([A-Z])", "_\\1", Drug) %>% gsub("^_", "", .)) %>%
    mutate(With_withoutDrug = ifelse(grepl(paste("_", distinct.drug, "_", sep = ""), Split_drugs),
                                     distinct.drug,
                                     paste("no ", distinct.drug, sep = ""))) %>%
    select(Drug, With_withoutDrug, everything())
  
} else {
  MTB.select.sub <- MTB.select %>%
    mutate(With_withoutDrug = ifelse(grepl(distinct.drug, Drug),
                                     distinct.drug,
                                     paste("no ", distinct.drug, sep = ""))) %>%
    select(Drug, With_withoutDrug, everything())
}
      
      
  MTB.select.sub <-     MTB.select.sub  %>%
  pivot_longer(
    cols = starts_with("AUC.0.168h_Iso."),
    names_to = "AUC_Isolate",
    values_to = "value"
  ) %>%
  drop_na()
  # iterate through list of variables for the associatiosn e.g AUC.0.168h_Iso.mc27000pbs
## Average of mc27000 and H37Ra | and average of mc27000pbs mc27000pan H37Rapbs


      MTB.select.sub.ExpoGrowing.intermedRes <-   MTB.select.sub %>%
        filter(AUC_Isolate ==  "AUC.0.168h_Iso.mc27000" | AUC_Isolate == "AUC.0.168h_Iso.H37Ra" )%>% # These were the strains used in the paper
        ungroup()%>%
        group_by(Drug)%>%
        mutate(mean_AUC_ExpoGrowth = mean(value))%>%
                ungroup()%>%
        select(With_withoutDrug,
               mean_AUC_ExpoGrowth)%>%
          ungroup()%>%
        distinct()%>%
        mutate(Drug = distinct.drug)
      
   MTB.select.growing.IntermedRes <- rbind( MTB.select.growing.IntermedRes,   MTB.select.sub.ExpoGrowing.intermedRes)
   
   
      MTB.select.sub.ExpoGrowing <-   MTB.select.sub %>%
        filter(AUC_Isolate ==  "AUC.0.168h_Iso.mc27000" | AUC_Isolate == "AUC.0.168h_Iso.H37Ra" )%>% # These were the strains used in the paper
        ungroup()%>%
        group_by(Drug)%>%
        mutate(mean_AUC_ExpoGrowth = mean(value))%>%
                ungroup()%>%
        select(With_withoutDrug,
               mean_AUC_ExpoGrowth)%>%
        ungroup()%>%
        distinct()%>%
           wilcox_test(
      formula = as.formula(paste( "mean_AUC_ExpoGrowth~ With_withoutDrug")),
           exact = TRUE)%>%
            select(-statistic)%>%
    mutate(Stat.test = "Mann.Whitney")%>%
    mutate(Drug.in.question = distinct.drug)%>%
        select(Drug.in.question,
               everything())
      
      # ------ Starved strain
       
      MTB.select.sub.Starved.intermedRes <-   MTB.select.sub %>%
       filter(AUC_Isolate ==  "AUC.0.168h_Iso.mc27000pbsStrvd" |
               AUC_Isolate == "AUC.0.168h_Iso.mc27000panStrvd2"    |
            AUC_Isolate == "AUC.0.168h_Iso.H37RapbsStrvd" 
             )%>% # These were the strains used in the paper
        ungroup()%>%
        group_by(Drug)%>%
        mutate(mean_AUC_Starved = mean(value))%>%
        ungroup()%>%
        select(With_withoutDrug,
               mean_AUC_Starved)%>%
        distinct()%>%
        mutate(Drug = distinct.drug)
      
      write.csv(       
      MTB.select.sub.Starved.intermedRes,
                paste("Intermediaty_Check_fig2/Starved_AUC_",
                      distinct.drug,".csv",sep=""),
      row.names = FALSE)
         
            MTB.select.starved.IntermedRes  <- rbind(MTB.select.starved.IntermedRes ,
                                                MTB.select.sub.Starved.intermedRes)

         
         #... Statistical mwu Test
      
         MTB.select.sub.Starved <-   MTB.select.sub %>%
       filter(AUC_Isolate ==  "AUC.0.168h_Iso.mc27000pbsStrvd" |
               AUC_Isolate == "AUC.0.168h_Iso.mc27000panStrvd2"    |
            AUC_Isolate == "AUC.0.168h_Iso.H37RapbsStrvd" 
             )%>% # These were the strains used in the paper
        ungroup()%>%
        group_by(Drug)%>%
        mutate(mean_AUC_Starved = mean(value))%>%
                   ungroup()%>%
        select(With_withoutDrug,
               mean_AUC_Starved)%>%

  distinct()%>%
    wilcox_test(
      formula = as.formula(paste( "mean_AUC_Starved ~ With_withoutDrug")),

       exact = TRUE
      
      )%>%
    select(-statistic)%>%
    mutate(Stat.test = "Mann.Whitney")%>%
    mutate(Drug.in.question = distinct.drug)%>%
        select(Drug.in.question,
               everything())
      
      MTB.select.stats <- rbind(MTB.select.stats,         MTB.select.sub.ExpoGrowing)
        MTB.select.stats <- rbind(MTB.select.stats,         MTB.select.sub.Starved )

      rm(MTB.select.sub.ExpoGrowing,
         MTB.select.sub.Starved)
    
  
}
      MTB.select.stats <-      MTB.select.stats %>%
   mutate(Drug.name= if_else(Drug.in.question == "E", "Ethambutol",
                             if_else(Drug.in.question == "H", "Isoniazid",
                   if_else(Drug.in.question == "R", "Rifampicin",
    if_else(Drug.in.question == "B", "Bedaquiline",
    if_else(Drug.in.question == "Pa", "Pretomanid",
    if_else(Drug.in.question == "C", "Clofazimine",
            if_else(Drug.in.question == "Su", "Sutezolid",
                    if_else(Drug.in.question == "P", "Rifapentin",
                            if_else(Drug.in.question == "Z","Pyrazinamid" ,
                                    if_else(Drug.in.question == "M","Moxifloxacin" ,
                                            if_else(Drug.in.question =="Sq", "Q109",
                                                    if_else(Drug.in.question == "D","Delamanid",
                                                           if_else(Drug.in.question == "L", "Linezolid", "Unkown") )))))))))))))
      rm(MTB.select.sub,
         MTB.select.sub.ExpoGrowing.intermedRes,
         MTB.select.sub.Starved.intermedRes)
```

# ggplotsupp fig 2
```{r}
MTB.select.starved.IntermedRes <- melt(MTB.select.starved.IntermedRes)
      MTB.select.growing.IntermedRes <- melt(      MTB.select.growing.IntermedRes)
MTB.select.both.Intermed  <- rbind(MTB.select.starved.IntermedRes ,
                                         MTB.select.growing.IntermedRes)



rm(MTB.select.starved.IntermedRes,
   MTB.select.growing.IntermedRes)

Label.of.drugs <- MTB.select.stats %>%
  select(Drug.in.question,
         Drug.name)%>%
  distinct()%>%
  mutate(Drug = Drug.in.question)%>%
  select(-Drug.in.question)

MTB.select.both.Intermed  <- left_join(MTB.select.both.Intermed ,
                                       Label.of.drugs)

MTB.select.both.Intermed  <-MTB.select.both.Intermed %>%
 mutate(With_withoutDrug2 = if_else(str_detect(With_withoutDrug, "no"), 
                                     paste("No", Drug.name, sep = " "), 
                                     Drug.name))

unique(MTB.select.both.Intermed$variable)

# Adding infromaiton on statistics
MTB.pval.select <- MTB.select.stats %>%
  select(Drug.in.question,
         .y.,
         p)%>%
  mutate(Drug = Drug.in.question,
         variable = .y.)%>%
  select(Drug,
         variable,
         p) %>%
  mutate(   p.value = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)) ) # Apply conditions

MTB.select.both.Intermed <- left_join(MTB.select.both.Intermed ,
                                      MTB.pval.select )
library(forcats)


MTB.select.both.Intermed %>%
  
  filter(variable == "mean_AUC_Starved")%>%
  mutate(With_withoutDrug2 = fct_relevel(With_withoutDrug2, 
                                         sort(unique(With_withoutDrug2[!str_detect(With_withoutDrug2, "No")])), 
                                         after = 0)) %>% # Places "No" values second
ggplot( aes(x = With_withoutDrug2, 
            y = value, 
            fill =variable)) +
        geom_boxplot(outlier.shape = NA, alpha = 0.8, size = 0.2) +
           
      
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
      
      
        geom_jitter(color = "black", size = 0.1, alpha = 1, shape = 20, position = position_jitter(seed = 1, width = 0.3, height = 0)) +
               
  
    scale_fill_manual(values = c("mean_AUC_Starved" = "darkgreen", 
                               "mean_AUC_ExpoGrowth" = "purple4")) +
  # Apply the  y-axis limits
   scale_y_continuous(limits = c(0.65, 0.95), breaks = seq(0.65, 0.95, by = 0.05)) +


        labs(
          x = "",
          y = "" ) +
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
               axis.text.x = element_text(size = 4, angle = 90, hjust = 1),

          axis.text.y = element_text(size = 4),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()
        ) +

       facet_grid( variable ~Drug.name + p.value,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed


 

```

```{r}
# Create the plot and assign it to a variable
plot_Supp_Fig_2a <- MTB.select.both.Intermed %>%
  filter(variable == "mean_AUC_Starved") %>%
  mutate(With_withoutDrug2 = fct_relevel(With_withoutDrug2, 
                                         sort(unique(With_withoutDrug2[!str_detect(With_withoutDrug2, "No")])), 
                                         after = 0)) %>%  # Places "No" values second
  ggplot(aes(x = With_withoutDrug2, 
             y = value, 
             fill = variable)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8, size = 0.2) +
  
  # Adding error bars at the ends of the quartile range
  stat_boxplot(geom = "errorbar", width = 0.1, size = 0.1) +
  
  geom_jitter(color = "black", size = 0.1, alpha = 1, shape = 20, 
              position = position_jitter(seed = 1, width = 0.3, height = 0)) +
  
  scale_fill_manual(values = c("mean_AUC_Starved" = "darkgreen", 
                               "mean_AUC_ExpoGrowth" = "purple4")) +
  
  # Apply the y-axis limits
  scale_y_continuous(limits = c(0.65, 0.95), breaks = seq(0.65, 0.95, by = 0.05)) +
  
  labs(x = "", y = "") +
  
  theme_prism(base_line_size = 0.2) +
  theme(
    strip.background = element_blank(),
    panel.border = element_blank(),
    legend.position = "none",
    strip.placement = "outside",
    aspect.ratio = 1,
    strip.text = element_text(size = 3),
    axis.text.x = element_text(size = 4, angle = 90, hjust = 1),
    axis.text.y = element_text(size = 4),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_blank()
  ) +
  
  facet_grid(variable ~ Drug.name + p.value, scales = "free_x", switch = "y", 
             labeller = labeller(.cols = label_wrap_gen(width = 100)))

# Save the plot as PDF on A4 size
ggsave("Supp.Fig.2b.pdf", plot = plot_Supp_Fig_2a, width = 8.27, height = 11.69, units = "in")

```

```{r}
# Create the plot and assign it to a variable
plot_Supp_Fig_2b <- MTB.select.both.Intermed %>%
  filter(variable ==  "mean_AUC_ExpoGrowth") %>%
  mutate(With_withoutDrug2 = fct_relevel(With_withoutDrug2, 
                                         sort(unique(With_withoutDrug2[!str_detect(With_withoutDrug2, "No")])), 
                                         after = 0)) %>%  # Places "No" values second
  ggplot(aes(x = With_withoutDrug2, 
             y = value, 
             fill = variable)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8, size = 0.2) +
  
  # Adding error bars at the ends of the quartile range
  stat_boxplot(geom = "errorbar", width = 0.1, size = 0.1) +
  
  geom_jitter(color = "black", size = 0.1, alpha = 1, shape = 20, 
              position = position_jitter(seed = 1, width = 0.3, height = 0)) +
  
  scale_fill_manual(values = c("mean_AUC_Starved" = "darkgreen", 
                               "mean_AUC_ExpoGrowth" = "purple4")) +
  
  # Apply the y-axis limits
  scale_y_continuous(limits = c(0.65, 0.95), breaks = seq(0.65, 0.95, by = 0.05)) +
  
  labs(x = "", y = "") +
  
  theme_prism(base_line_size = 0.2) +
  theme(
    strip.background = element_blank(),
    panel.border = element_blank(),
    legend.position = "none",
    strip.placement = "outside",
    aspect.ratio = 1,
    strip.text = element_text(size = 3),
    axis.text.x = element_text(size = 4, angle = 90, hjust = 1),
    axis.text.y = element_text(size = 4),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_blank()
  ) +
  
  facet_grid(variable ~ Drug.name + p.value, scales = "free_x", switch = "y", 
             labeller = labeller(.cols = label_wrap_gen(width = 100)))

# Save the plot as PDF on A4 size
ggsave("Supp.Fig.2a.pdf", plot = plot_Supp_Fig_2b, width = 8.27, height = 11.69, units = "in")

```

```{r}
 rm(
    MTB.select,
    plot_Supp_Fig_2b,
    plot_Supp_Fig_2a,
    MTB.stats.wide,
    MTB.select.stats, 
    MTB.pval.select,
    MTB.select.both.Intermed)
```

# Supplementary Fig 4
# Plot Box plots  of e.g. min MIC of H37Ra (y) vs SOC and Better than SOC with association scores 
```{r}
MTB.mic <- Main.df %>%
  select(Drug,
         RMM.2021,
         BMM.2021,
         BMM.BHeB.2021,
         Clinical.2022,
          matches("lg2."))
# Please in this step only process Iso.mc27000
list.of.Isolates <- c("Iso.mc27000")

list.of.models <- c("RMM.2021",
                    "BMM.2021",
                    "BMM.BHeB.2021",
                    "Clinical.2022" )

mod <- list.of.models[1]
iso <- list.of.Isolates[1]

list.of.calculations <- c("min",
                    "mean*",
                    "median")

calc <- list.of.calculations[1]
gg.plot.list <- list()
```

## building gg.plot list for Iso.mc27000
```{r}
for ( iso in list.of.Isolates ) {
  
  MTB.mic.sub <- MTB.mic %>%
    select(Drug,
           RMM.2021,
           BMM.2021,
           BMM.BHeB.2021,
           Clinical.2022,
           matches(iso))
  
  for( calc in list.of.calculations ) {
    
    # Relapsing Mouse model 2021
    
      MTB.mic.sub.RMM <-  MTB.mic.sub %>%
        select(Drug,
               RMM.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(RMM.2021 = case_when(
    RMM.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = RMM.2021)%>%
        mutate(In.vivo.Model = "Relapsing")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.RMM <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "RMM.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.RMM <-  MTB.mic.sub.RMM %>%
         mutate(p = pval.RMM$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.RMM$Outcome <- factor(      MTB.mic.sub.RMM$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))

       rm(pval.RMM)
       
      ##  ggplot RMM
      gg.RMM <- ggplot(MTB.mic.sub.RMM, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
     #  y = bquote(atop(mc^2 * " 700", atop(.(calc), "MIC (Log2)")))) +  # Using atop for new lines
      y = paste("mc² 7000\n", calc, "\nMIC (Log2)", sep = "")) +  # Using paste for consistent text
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()
        ) +

       facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc, "RMM", sep = "_")
      gg.plot.list [[plot_key]] <-      gg.RMM
      
      
      rm(gg.RMM,
         MTB.mic.sub.RMM)

  #----- BMM 
      
      
      MTB.mic.sub.BMM <-  MTB.mic.sub %>%
        select(Drug,
               BMM.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(BMM.2021 = case_when(
    BMM.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = BMM.2021)%>%
        mutate(In.vivo.Model = "Bactericidal")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.BMM <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "BMM.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.BMM <-  MTB.mic.sub.BMM %>%
         mutate(p = pval.BMM$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.BMM$Outcome <- factor(      MTB.mic.sub.BMM$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))

    
      gg.BMM <- ggplot(MTB.mic.sub.BMM, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                    width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "BMM",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.BMM
      
      
      rm(gg.BMM,
         pval.RMM,
         pval.BMM,
         MTB.mic.sub.BMM)
      
    # BBM granulomatous
      
      MTB.mic.sub.BMM.BHeB <-  MTB.mic.sub %>%
        select(Drug,
               BMM.BHeB.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(BMM.BHeB.2021 = case_when(
    BMM.BHeB.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = BMM.BHeB.2021)%>%
        mutate(In.vivo.Model = "Bactericidal granulomatous")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.BMM.BHeB <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "BMM.BHeB.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.BMM.BHeB <-  MTB.mic.sub.BMM.BHeB %>%
         mutate(p = pval.BMM.BHeB$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.BMM.BHeB$Outcome <- factor(      MTB.mic.sub.BMM.BHeB$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))
    
      gg.BMM.BHeB <- ggplot(MTB.mic.sub.BMM.BHeB, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "BMM.BHeB",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.BMM.BHeB
      
      
      rm(gg.BMM.BHeB,
         MTB.mic.sub.BMM.BHeB)
      
      # Clinical trial  ---------
      MTB.mic.sub.Clinical <-  MTB.mic.sub %>%
        select(Drug,
               Clinical.2022,
               matches(calc))%>%
        drop_na()%>%
        filter(Clinical.2022 != "ND")%>%
        filter(Clinical.2022 != "C2-")%>%
        mutate(Clinical.2022 = case_when(
    Clinical.2022 %in% c( "C1-") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = Clinical.2022)%>%
        mutate(In.vivo.Model = "Clinical trial")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.Clinical <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "Clinical.2022"))  # Filter based on both patterns
        
        
       MTB.mic.sub.Clinical <-  MTB.mic.sub.Clinical %>%
         mutate(p = pval.Clinical$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.Clinical$Outcome <- factor(      MTB.mic.sub.Clinical$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))
    
      gg.Clinical <- ggplot(MTB.mic.sub.Clinical, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "Clinical",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.Clinical
      
      
      rm(gg.Clinical,
         MTB.mic.sub.Clinical)
      
      
    
    
  }
  
}


```


## building gg.plot list for Iso.H37Ra
```{r}

list.of.Isolates <- c("Iso.H37Ra")

for ( iso in list.of.Isolates ) {
  
  MTB.mic.sub <- MTB.mic %>%
    select(Drug,
           RMM.2021,
           BMM.2021,
           BMM.BHeB.2021,
           Clinical.2022,
           matches(iso))
  
  for( calc in list.of.calculations ) {
    
    # Relapsing Mouse model 2021
    
      MTB.mic.sub.RMM <-  MTB.mic.sub %>%
        select(Drug,
               RMM.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(RMM.2021 = case_when(
    RMM.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = RMM.2021)%>%
        mutate(In.vivo.Model = "Relapsing")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.RMM <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "RMM.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.RMM <-  MTB.mic.sub.RMM %>%
         mutate(p = pval.RMM$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.RMM$Outcome <- factor(      MTB.mic.sub.RMM$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))

       rm(pval.RMM)
       
      ##  ggplot RMM
      gg.RMM <- ggplot(MTB.mic.sub.RMM, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
     #  y = bquote(atop(mc^2 * " 700", atop(.(calc), "MIC (Log2)")))) +  # Using atop for new lines
      y = paste("H37Ra\n", calc, "\nMIC (Log2)", sep = "")) +  # Using paste for consistent text
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()
        ) +

       facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc, "RMM", sep = "_")
      gg.plot.list [[plot_key]] <-      gg.RMM
      
      
      rm(gg.RMM,
         MTB.mic.sub.RMM)

  #----- BMM 
      
      
      MTB.mic.sub.BMM <-  MTB.mic.sub %>%
        select(Drug,
               BMM.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(BMM.2021 = case_when(
    BMM.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = BMM.2021)%>%
        mutate(In.vivo.Model = "Bactericidal")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.BMM <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "BMM.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.BMM <-  MTB.mic.sub.BMM %>%
         mutate(p = pval.BMM$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.BMM$Outcome <- factor(      MTB.mic.sub.BMM$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))

    
      gg.BMM <- ggplot(MTB.mic.sub.BMM, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                    width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "BMM",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.BMM
      
      
      rm(gg.BMM,
         pval.RMM,
         pval.BMM,
         MTB.mic.sub.BMM)
      
    # BBM granulomatous
      
      MTB.mic.sub.BMM.BHeB <-  MTB.mic.sub %>%
        select(Drug,
               BMM.BHeB.2021,
               matches(calc))%>%
        drop_na()%>%
        mutate(BMM.BHeB.2021 = case_when(
    BMM.BHeB.2021 %in% c("C0", "-C1", "-C2") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = BMM.BHeB.2021)%>%
        mutate(In.vivo.Model = "Bactericidal granulomatous")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.BMM.BHeB <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "BMM.BHeB.2021"))  # Filter based on both patterns
        
        
       MTB.mic.sub.BMM.BHeB <-  MTB.mic.sub.BMM.BHeB %>%
         mutate(p = pval.BMM.BHeB$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.BMM.BHeB$Outcome <- factor(      MTB.mic.sub.BMM.BHeB$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))
    
      gg.BMM.BHeB <- ggplot(MTB.mic.sub.BMM.BHeB, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "BMM.BHeB",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.BMM.BHeB
      
      
      rm(gg.BMM.BHeB,
         MTB.mic.sub.BMM.BHeB)
      
      # Clinical trial  ---------
      

      
      MTB.mic.sub.Clinical <-  MTB.mic.sub %>%
        select(Drug,
               Clinical.2022,
               matches(calc))%>%
        drop_na()%>%
        filter(Clinical.2022 != "ND")%>%
        filter(Clinical.2022 != "C2-")%>%
        mutate(Clinical.2022 = case_when(
    Clinical.2022 %in% c( "C1-") ~ "Standard of Care",
    TRUE ~ "Better than SOC"))%>%
        mutate(Isolate = iso,
               Calculation = calc)%>%
        mutate(Outcome = Clinical.2022)%>%
        mutate(In.vivo.Model = "Clinical trial")%>%
         mutate(value = select(., matches(calc))[[1]])%>%
        select(Isolate,
              Calculation,
              In.vivo.Model,
               Drug,
               Outcome,
             value)
      
      # Add p values
        pval.Clinical <- MTB.stats %>%
        select(.y.,
                 In.vivo.outcome,
                 p)%>%
          filter(str_detect(.y., iso) & str_detect(.y., calc) & str_detect(In.vivo.outcome,
                                                                           "Clinical.2022"))  # Filter based on both patterns
        
        
       MTB.mic.sub.Clinical <-  MTB.mic.sub.Clinical %>%
         mutate(p = pval.Clinical$p)%>%
         mutate(p = ifelse(p < 0.0001, "P < 0.0001", paste("P =", p)))
   
             MTB.mic.sub.Clinical$Outcome <- factor(      MTB.mic.sub.Clinical$Outcome, 
                                                     levels = c("Standard of Care", "Better than SOC"))
    
      gg.Clinical <- ggplot(MTB.mic.sub.Clinical, 
                       aes(x = Outcome, 
                           y = value, 
                           fill = Outcome)) +
        geom_boxplot(outlier.shape = NA,
                     alpha = 0.5,
                     size = 0.2) +
           
      # Adding error bars at the ends of the quartile range
           stat_boxplot(geom = "errorbar",
                        width = 0.1, 
                        size = 0.1) +
              geom_jitter(color = "black", 
                          size = 0.3, 
                          alpha = 1, 
                          shape = 20, 
                          position = position_jitter(seed = 1, 
                                                     width = 0.3, 
                                                     height = 0)) +
                 scale_fill_manual(values = c("Standard of Care" = "coral",
                                              "Better than SOC" = "darkgreen")) +
    scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5))+  # Set y-axis limits and intervals
        labs(
          x = "",
          y = "") +  
        theme_prism(base_line_size = 0.2) +
        theme(
          strip.background = element_blank(),
          panel.border = element_blank(),
          legend.position = "none",
          strip.placement = "outside",
          aspect.ratio = 1,
          strip.text = element_text(size = 3),
         axis.text.x = element_blank(),
          axis.text.y = element_text(size = 2),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_blank(),
               axis.text = element_blank()) +
        facet_grid( ~  In.vivo.Model + p ,
                   scales = "free_x",
                   switch = "y",
                   labeller = labeller(.cols = label_wrap_gen(width = 100))) # Adjust width as needed
    
      plot_key <- paste(iso, calc,
                        "Clinical",
                        sep = "_")
      
      gg.plot.list [[plot_key]] <-gg.Clinical
      
      
      rm(gg.Clinical,
         MTB.mic.sub.Clinical)
      
  }
  
}
```


# Plot list of plot
```{r}

# Load the package
library(gridExtra)


plot.path <- paste0(info.resDir, "/", "ASCTsupp.fig4.pdf")


# Open a PDF device to save the plots
pdf(plot.path, width = 11, height = 8.5) # Set the dimensions as per your requirement


grid.arrange(grobs = gg.plot.list, nrow = 6, ncol = 4, top = NULL)


# Close the PDF device
dev.off()

```



