
# Aim: 
Load each tracking output file, find the total number of tracked cells per well, then per experiment, then for whole ASCT tolerance experiment.

# Section 1: Defining paths and variables
```{r setup, include=FALSE}

# Working directory
genDir <- getwd() 
setwd(genDir)

start <- Sys.time()
results.dir <- paste(genDir,
                     "/",
                     "ASCT_Experimental_Results/",
                     sep="")
# ASCT experiments you wish to curate

res.export <- paste(genDir,
                    "/Fig_results/",
                    sep="")

#ASCT experiments you wish to curate
#Fitting norm
list.of.experiments.for.loop <- c("ASCT.04_MXF20x",
                                  "ASCT.07_TGC20x",
                                   "ASCT.08_AMK20x",
                                  "ASCT.09_LZD20x",
                                  "ASCT.13_AMK10x",
                                  "ASCT.14_MIN20x",

                                  "ASCT.16_TGC10x",
                                  "ASCT.18_AZM10x",
                                  "ASCT.19_LZD10x",
                                  "ASCT.20_MIN10x",
                                  "ASCT.22_AZM20x",
                                  "ASCT.24_MXF10x",
                                  "ASCT.03_FOX20x",
                                  "ASCT.05_IPM10x",
                                   "ASCT.06_FOX10x",
                                  "ASCT.23_IPMc20x"
                                   )


exp.sub.dir <- c("/ASCT_Data/PerWell-Trk.n.Results")


# label directory file information to be used in Section 4  clinical isolates list
# Navigate back one directory (assuming you want to go up one level)
label_dir <- file.path(genDir, "..")

# Enter the ASCT.Ranalysis_Exp_Info directory
label_dir <- file.path(label_dir , "ASCT.Ranalysis_Exp_Info")

# Enter the ASCT_CC directory
label_dir <- file.path(label_dir , "ASCT_Label_directory")

clinical.iso.list.file <- c("ASCT_1_Clinical.iso_list.csv")


```

# Section 2: Loading libraries
```{r}
library(ggpubr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggforce)
library(RColorBrewer)
library(platetools)
library(directlabels) 
library(MESS)
library(gghighlight)
library(reshape2)
library(scales)

library(ggprism)

```


# Section 3: Loading list of killing feature tables
```{r}
#id <-list.of.experiments.for.loop[1]

Total.N.df <- data.frame()
## Loop through each exp.ID
for (id in list.of.experiments.for.loop ) {
  
  
  print(id)
 
  # Create the path to your desired directory for the current exp.ID
  path <- file.path("..","..","ASCT_EXPERIMENTS_v2-critical",id, exp.sub.dir)
  
  # List all files in the directory
  files <- list.files(path)
  
  # Filter files that contain "Clinical.Isolates" and "Killing.Features" in their names
  matching_files <- files[grep("_Trkv2_LC.N.csv", files)]
  
  # Load the matching CSV files
  data <- lapply(matching_files, function(file) {
    read.csv(file.path(path, file))
  })
  

  # Assuming your list of dataframes is called 'df_list'
summarized_df <- bind_rows(  data) %>%
  select(timestep, Exp, Well_coordinate, live.dead.def, Trkv2_Ila.Def.2_LC.N) %>%
  filter(timestep == 0)%>%
  ungroup()%>%
  group_by(Exp,
          Well_coordinate) %>%
  summarize(total_Trkv2_Ila_Def_2_LC_N = sum(Trkv2_Ila.Def.2_LC.N, na.rm = TRUE))%>%
    mutate(Exp = sub("_.*", "", Exp))

  


rm(data)

Total.N.df  <- rbind(Total.N.df ,
                     summarized_df)


}


```
```{r}
rm(summarized_df)
```


```{r}
All.data <- sum(Total.N.df$total_Trkv2_Ila_Def_2_LC_N)
All.data
perExp <- All.data/16
perExp

perWell <- perExp/1260
perWell

Total.N.df <- Total.N.df %>%
  mutate(ExpFile = Exp)%>%
  select(-Exp)
```


# Load QC results table
```{r}
QC.df <- read.csv("/Users/jovanovic/Documents/PhD/Project_Tolerance/Ranalysis/ASCT/ASCT_Figures/ASCT_TrackingResultsTable_Growth.Reproducibity.Numbers.Mahalanobis/Fig_results/ASCTmab_QC.results.table_20241003_0550.csv")

QC.df <- QC.df %>%
  select(Isolate,
         Abx.con,
         Well_coordinate,
         ExpFile,
         QC_Growth_growth.1_nogrowth.0,
         QC_TrackNumber_less1K.1_more1K.0,
         QC_Reproducibility_outlier.1_reproducible.0,
         QC_Low.initial.LCF.across.all.def_less80perc.1_more80perc.0,
         QC_Iso.too.few.numbers_low.1_high.0,
         QC_Exclude.Iso.from.Analysis_exclude.1_include.0)
```

## perWell
```{r}


Total.N.df.perWell <- left_join(Total.N.df,
                                QC.df)


Total.N.df.perWell.ExclGrowth <- Total.N.df.perWell %>%
  filter(QC_Growth_growth.1_nogrowth.0 == 0)


Total.N.df.perWell.OnlyInclded <- Total.N.df.perWell %>%
  filter(QC_Growth_growth.1_nogrowth.0 == 0 &
            QC_TrackNumber_less1K.1_more1K.0 == 0 & 
              QC_Reproducibility_outlier.1_reproducible.0 == 0 &
                QC_Low.initial.LCF.across.all.def_less80perc.1_more80perc.0 == 0 &
                    QC_Low.initial.LCF.across.all.def_less80perc.1_more80perc.0== 0 & QC_Exclude.Iso.from.Analysis_exclude.1_include.0 == 0 )%>%
    mutate(GrowthExclOnly.analysisOnly = "Analysis.Incl.wells")%>%
  select(Exp,
         Isolate,
         Abx.con,
         Well_coordinate,
         GrowthExclOnly.analysisOnly ,
         total_Trkv2_Ila_Def_2_LC_N )


Total.N.df.perWell.Exl.Incl <- Total.N.df.perWell.ExclGrowth %>%
  mutate(GrowthExclOnly.analysisOnly = "Growth.Excl.wells")%>%
  select(Exp,
         Isolate,
         Abx.con,
         Well_coordinate,
         GrowthExclOnly.analysisOnly ,
         total_Trkv2_Ila_Def_2_LC_N )

Total.N.df.perWell.Exl.Incl <- rbind(Total.N.df.perWell.Exl.Incl ,
                                    Total.N.df.perWell.OnlyInclded )


# Reorder the levels of GrowthExclOnly.analysisOnly
Total.N.df.perWell.Exl.Incl$GrowthExclOnly.analysisOnly <- factor(
  Total.N.df.perWell.Exl.Incl$GrowthExclOnly.analysisOnly, 
  levels = c("Growth.Excl.wells", "Analysis.Incl.wells")  # Set desired order
)

today <-  Sys.time()
today  <- format(today , "%Y%m%d%H")


Plot.filepath <- paste(res.export,

                       "ASCTsupp_Histogram.total.number.of.tracked.cells_growth.excl.only_analaysis.incl_",
                       
                       today ,
                       ".pdf",sep="")
pdf(Plot.filepath)



# Assuming your data is stored in a tibble called df
ggplot(Total.N.df.perWell.Exl.Incl, aes(x = total_Trkv2_Ila_Def_2_LC_N, 
                                        fill = GrowthExclOnly.analysisOnly)) +
  geom_histogram(binwidth = 250, 
                 color = alpha("black", 0.4),  # Faint black outline
                                  size = 0.1,                  # Reduces the thickness of the outline

                 alpha = 0.75) +
  labs(title = "Histogram of number of tracked cells per well",
       x = "Number of tracked cells",
       y = "Frequency") +
  scale_x_continuous(limits = c(0, 30000), breaks = seq(0, 30000, by = 10000)) +
  scale_fill_manual(values = c("Analysis.Incl.wells" = "coral", 
                               "Growth.Excl.wells" = "steelblue")) +
  theme_prism(base_line_size = 8/14) +
   theme(legend.position = "none",
       
        axis.ticks.x = element_blank(), # Remove x-axis tick marks
        axis.ticks.y = element_blank() # Remove y-axis tick marks
) + # Set y-axis label size

  facet_wrap(~ GrowthExclOnly.analysisOnly)



dev.off()



```


```{r}
#rm(Total.N.df2)
Total.N.df2 <- left_join(Total.N.df,
                        QC.df)

Total.N.df.perWell <- Total.N.df2 %>%
  ungroup()%>%
  select(-Exp)

Total.N.df2 <-Total.N.df2 %>%
  filter(QC_Growth_growth.1_nogrowth.0 == 0)%>%
    filter(QC_TrackNumber_less1K.1_more1K.0 == 0)


Total.N.df2 <- Total.N.df2  %>%
  ungroup()%>%
  group_by(ExpFile,
           Abx.con,
           Isolate)%>%
  mutate(Isolate_drug.pair.N = sum(total_Trkv2_Ila_Def_2_LC_N))%>%
  ungroup()%>%
  select(ExpFile,
         Abx.con,
         Isolate,
         Isolate_drug.pair.N)%>%
  distinct()

```

# Find the sum of Isolates-drug of remaining isolates
```{r}


Total.N.df2 <- Total.N.df2 %>%
  mutate(Drug_Iso = paste(Abx.con,
                          Isolate,sep="_"))


str(Total.N.df2)
```

# Plot histogram
```{r}

min(Total.N.df2$Isolate_drug.pair.N)
max(Total.N.df2$Isolate_drug.pair.N)



today <-  Sys.time()



today  <- format(today , "%Y%m%d%H")


Plot.filepath <- paste(res.export,

                       "ASCTsupp_Histogram.total.number.of.tracked.cells_",
                       
                       today ,
                       ".pdf",sep="")
pdf(Plot.filepath)



# Assuming your data is stored in a tibble called df
ggplot(Total.N.df2, aes(x = Isolate_drug.pair.N)) +
  geom_histogram(binwidth = 500, 
                 fill = "blue",
                 color = "black",
                 alpha = 0.7) +
  labs(title = "Histogram of Isolate Drug Pair N",
       x = "Isolate Drug Pair N",
       y = "Frequency") +
  scale_x_continuous(limits = c(0, 80000), breaks = seq(0, 80000, by = 10000)) +

  theme_prism(base_line_size = 8/14)


dev.off()

```


#label
```{r}

# Sort the data by Isolate_drug.pair.N in descending order and select the top 5 isolates
top_5 <- Total.N.df2 %>%
  mutate(Isolate = gsub("Iso.ATc.19979", "ATCC",Isolate))%>%
  mutate(Isolate =gsub("Iso.","",Isolate))%>%
  mutate(Iso_drug = paste(Isolate,
                          Abx.con ,sep ="_"))%>%
  arrange(desc(Isolate_drug.pair.N)) %>%
  head(10)



Plot.filepath <- paste(res.export,

                       "ASCTsupp_Histogram.total.number.of.tracked.cells_LABELS_",
                       
                       today ,
                       ".pdf",sep="")
pdf(Plot.filepath)

# Create the histogram and label the 5 furthest bins
ggplot(Total.N.df2, aes(x = Isolate_drug.pair.N)) +
  geom_histogram(binwidth = 500, 
                 fill = "blue",
                 color = "black",
                 alpha = 0.7) +
  labs(title = "Histogram of Isolate Drug Pair N",
       x = "Isolate Drug Pair N",
       y = "Frequency") +
  scale_x_continuous(limits = c(0, 80000), breaks = seq(0, 80000, by = 10000)) +
  theme_prism(base_line_size = 8/14) +
  
  # Add labels for the 5 furthest bins using geom_text
  geom_text(data = top_5, 
            aes(x = Isolate_drug.pair.N, 
                y = 0, 
                label = Iso_drug), 
                        position = position_jitter(width = 2000, height = 5), # Jitter in both x and y direction

            vjust = -3, 
            angle = 0,     # Rotate the text at a 45-degree angle
            size = 1, 
            color = "black") 

dev.off()

```

